---
title: 'List of gng runs and IDs to exclude from analyses'
author: 'Krista DeStasio'
date: '10/25/2018'
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: no
  pdf_document:
    toc: yes
    toc_depth: '3'
  word_document:
    toc: yes
    toc_depth: '3'
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
## R version 3.4.3 ##
rm(list = ls())
setwd('~/Desktop/REV_scripts/behavioral/gng/scripts/analyses/')
output_dir = '~/Desktop/REV_scripts/behavioral/gng/output/'

## Install and load required packages
list.of.packages <- c('reshape2', 'knitr', 'lme4', 'sjPlot', 'sjmisc', 'tidyverse', 'lme4', 'lmerTest', 'ez', 'gridExtra')
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,'Package'])] 
if (length(new.packages)) install.packages(new.packages, repos = 'http://cran.us.r-project.org') 
lapply(list.of.packages, library, character.only = TRUE)

knitr::opts_chunk$set(fig.width = 12, fig.height = 8, fig.path = 'Figs/', echo = TRUE, warning = FALSE, message = FALSE)
```

```{r Create the participant ID and condition variables, include=FALSE}
ID <- as.factor(c(1:144)) # Create the subject ID column
cond <- c(0, 1, 0, 0, 0, 1, 1, 0, 1, 0, 0, 1, 1, 1, 1, 1, 0, 0, 1, 0, 1, 1, 1, 0, 1, 1, 0, 0, 0, 1, 1, 1, 1, 0, 1, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 1, 0, 1, 0, 1, 1, 0, 0, 0, 1, 1, 1, 0, 1, 0, 1, 1, 1, 0, 0, 0, 0, 0, 1, 0, 0, 1, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 1, 1, 0, 1, 1, 0, 1, 0, 1, 1, 1, 1, 0, 0, 1, 1, 1, 1, 1, 0, 0, 1, 1, 1, 1, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 1, 0, 1, 1, 0, 0, 1, 0, 1, 1, 0, 1, 1, 1, 0, 0, 1, 0) # Match the participant to their condition
condition <- factor(cond, labels = c('Control', 'Training'))
```

```{r Read in the data, include=FALSE}
# Counts
CorrTotal <- read.table(paste0(output_dir, 'gng_Corr_Count.txt')) # All stimuli, all trial types
CorrGo <- read.table(paste0(output_dir, 'gng_CorrGo_Count.txt')) # All stimuli, go trials
CorrNoGo <- read.table(paste0(output_dir, 'gng_CorrNoGo_Count.txt')) # All stimuli, no-go trials
IncorrGo <- read.table(paste0(output_dir, 'gng_IncorrGo_Count.txt')) # All stimuli, go trials
IncorrNoGo <- read.table(paste0(output_dir, 'gng_IncorrNoGo_Count.txt')) # All stimuli, no-go trials
CorrNoGo_Risk <- read.table(paste0(output_dir, 'gng_CorrNoGo_Count_Risk.txt')) # PRC stimuli, no-go trials
IncorrNoGo_Risk <- read.table(paste0(output_dir, 'gng_IncorrNoGo_Count_Risk.txt')) # PRC stimuli, no-go trials
IncorrNoGo_Neutral <- read.table(paste0(output_dir, 'gng_IncorrNoGo_Count_Neutral.txt')) # Neutral stimuli, no-go trials

# Response times
CorrGoRT_Risk <- read.table(paste0(output_dir, 'gng_CorrGo_RT_Risk.txt'))
CorrGoRT_Neutral <- read.table(paste0(output_dir, 'gng_CorrGo_RT_Neutral.txt'))
CorrGoRT_Total <- read.table(paste0(output_dir, 'gng_CorrGo_RT.txt'))
IncorrNoGoRT <- read.table(paste0(output_dir, 'gng_IncorrNoGo_RT.txt'))

# Wrong go's by block
block1_IncorrGo <- read.table(paste0(output_dir, 'GNG_IncorrGo_CountByBlock_run1.txt'))
block2_IncorrGo <- read.table(paste0(output_dir, 'GNG_IncorrGo_CountByBlock_run2.txt'))
block3_IncorrGo <- read.table(paste0(output_dir, 'GNG_IncorrGo_CountByBlock_run3.txt'))
block4_IncorrGo <- read.table(paste0(output_dir, 'GNG_IncorrGo_CountByBlock_run4.txt'))
block5_IncorrGo <- read.table(paste0(output_dir, 'GNG_IncorrGo_CountByBlock_run5.txt'))
```

```{r Put data frames in long form, include=FALSE}
# Make a vector containing all the dataframes
dfs <- c('CorrGo', 'CorrTotal', 'CorrNoGo', 'CorrNoGo_Risk', 'IncorrGo', 'IncorrNoGo', 'IncorrNoGo_Risk', 'IncorrNoGo_Neutral', 'CorrGoRT_Risk', 'CorrGoRT_Neutral', 'CorrGoRT_Total', 'IncorrNoGoRT', 'block1_IncorrGo', 'block2_IncorrGo', 'block3_IncorrGo', 'block4_IncorrGo', 'block5_IncorrGo')

# Name the columns for each data frame by the run number
for (df in dfs) {
  df.tmp <- get(df)
  names(df.tmp) <- c('run1', 'run2', 'run3', 'run4')
  assign(df, df.tmp)
}

# Append the participant IDs and conditions to the front of each data frame
for (df in dfs) {
    df.tmp <- get(df)
    df.tmp <- cbind(ID, condition, df.tmp)
    assign(df, df.tmp)
}

# Put the data frames in long form and append '_long' to the data frame name
for (df in dfs) {
    df.tmp <- get(df)
    df.tmp <- melt(data = df.tmp, idvars = ID, measure.vars = c('run1', 'run2','run3', 'run4'), variable.name = 'run_number', value.name = df)
    assign(paste(df, '_long', sep = ''),df.tmp)
}
```
    
```{r Create a single data frame, include=FALSE}
# Get count for each stim type  
df_gng <- cbind(CorrGo_long, CorrTotal_long[,4], CorrNoGo_long[,4], CorrNoGo_Risk_long[,4], IncorrGo_long[,4], IncorrNoGo_long[,4], IncorrNoGo_Risk_long[,4], IncorrNoGo_Neutral_long[,4], CorrGoRT_Risk_long[,4], CorrGoRT_Neutral_long[,4], CorrGoRT_Total_long[,4], IncorrNoGoRT_long[,4], block1_IncorrGo_long[,4], block2_IncorrGo_long[,4], block3_IncorrGo_long[,4], block4_IncorrGo_long[,4], block5_IncorrGo_long[,4])

colnames(df_gng) <- c('ID', 'Condition', 'run_number', 'CorrGo', 'CorrTotal', 'CorrNoGo', 'CorrNoGo_Risk', 'IncorrGo', 'IncorrNoGo', 'IncorrNoGo_Risk', 'IncorrNoGo_Neutral', 'CorrGoRT_Risk', 'CorrGoRT_Neutral', 'CorrGoRT_Total', 'IncorrNoGo_RT', 'block1_IncorrGo', 'block2_IncorrGo', 'block3_IncorrGo', 'block4_IncorrGo', 'block5_IncorrGo') 

# Sanity check
# for (i in 1:length(df_gng)) {
#     print(df_gng[i, 'IncorrGo'] == (sum(df_gng[i,16:length(df_gng)])))
# }

# Subset blocks, long format
data_byblock <- melt(data = df_gng[,c(1:3, 16:length(df_gng))], idvars = ID, measure.vars = c('block1_IncorrGo', 'block2_IncorrGo','block3_IncorrGo', 'block4_IncorrGo', 'block5_IncorrGo'), variable.name = 'block')

# Replace NaNs with Na
data_byblock[ is.na(data_byblock) ] <- NA
df_gng[ is.na(df_gng) ] <- NA

# Make a column to specify whether scores are from the base scan (pre) or end scan (post)
df_gng$Scan <- ifelse(df_gng$run_number %in% c('run1', 'run2'), 'pre', ifelse(df_gng$run_number %in% c('run3', 'run4'), 'post', NA))
```

# Plots
```{r, include=FALSE}
incorrGo_base <- ggplot(subset(df_gng, run_number %in% c('run1', 'run2'))) +
    aes(x = run_number, y = IncorrGo, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Base Scan \nRaw Data, All Participants')
incorrGo_end <- ggplot(subset(df_gng, run_number %in% c('run3', 'run4'))) +
    aes(x = run_number, y = IncorrGo, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During End Scan \nRaw Data, All Participants')

incorrNoGo_base <- ggplot(subset(df_gng, run_number %in% c('run1', 'run2'))) +
    aes(x = run_number, y = IncorrNoGo, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect No Go Count During Base Scan \nRaw Data, All Participants')
incorrNoGo_end <- ggplot(subset(df_gng, run_number %in% c('run3', 'run4'))) +
    aes(x = run_number, y = IncorrNoGo, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During End Scan \nRaw Data, All Participants')

incorrGo_byBlock_run1 <- ggplot(subset(data_byblock, run_number %in% c('run1'))) +
    aes(x = block, y = value, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Each Block \nRun 1, All Participants')
incorrGo_byBlock_run2 <- ggplot(subset(data_byblock, run_number %in% c('run2'))) +
    aes(x = block, y = value, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Each Block \nRun 2, All Participants')
incorrGo_byBlock_run3 <- ggplot(subset(data_byblock, run_number %in% c('run3'))) +
    aes(x = block, y = value, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Each Block \nRun 3, All Participants')
incorrGo_byBlock_run4 <- ggplot(subset(data_byblock, run_number %in% c('run4'))) +
    aes(x = block, y = value, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Each Block \nRun 4, All Participants')

```
```{r, echo = FALSE}
grid.arrange(incorrGo_base, incorrGo_end, ncol = 2)
grid.arrange(incorrNoGo_base, incorrNoGo_end, ncol = 2)
grid.arrange(incorrGo_byBlock_run1, incorrGo_byBlock_run2, ncol = 2) 
grid.arrange(incorrGo_byBlock_run3, incorrGo_byBlock_run4, ncol = 2)
```

# Remove outliers
Remove runs in which a participant has more than 25 incorrect go responses in any given block.  
```{r, echo=FALSE}
# I know this is terrible - quick & dirty. I'm so sorry. I promise to come back and fix this!

clean_df_gng <- df_gng
clean_df_gng <- clean_df_gng %>%
    mutate(CorrGo = replace(CorrGo, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(CorrTotal = replace(CorrTotal, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(CorrNoGo = replace(CorrNoGo, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(CorrNoGo_Risk = replace(CorrNoGo_Risk, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(IncorrGo = replace(IncorrGo, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(IncorrNoGo = replace(IncorrNoGo, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(IncorrNoGo_Risk = replace(IncorrNoGo_Risk, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(IncorrNoGo_Neutral = replace(IncorrNoGo_Neutral, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(CorrGoRT_Risk = replace(CorrGoRT_Risk, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(CorrGoRT_Neutral = replace(CorrGoRT_Neutral, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(CorrGoRT_Total = replace(CorrGoRT_Total, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))
clean_df_gng <- clean_df_gng %>%
    mutate(IncorrNoGo_RT = replace(IncorrNoGo_RT, 
                            which(block1_IncorrGo >= 25 | 
                                      block2_IncorrGo >= 25 | 
                                      block3_IncorrGo >= 25 |  
                                      block4_IncorrGo >= 25 | 
                                      block5_IncorrGo >= 25), NA))

clean_df_blocks <- data_byblock %>% 
    mutate(value = replace(value, 
                           which(value >= 25), NA))
```



Runs to remove (or fix?):

Subject  | Run (acq) | Reason 
-------- | --- | ------- 
116      |  1  | Switching go/no-go stimuli (remove)
106      |  2  | Sleeping & responding to wrong categories (remove)
019      |  3  | Sleeping throughout (remove)
002      |  2  | Reversed response categories toward end
006      |  3  | Reversed categories in blocks 2 and 4
009      |  2  | Reversed categories in first block
013      |  2  | Reversed categories
014      |  2  | Reversed categories

# Plot without outliers
```{r, include=FALSE}
incorrGo_base <- ggplot(subset(clean_df_gng, run_number %in% c('run1', 'run2'))) +
    aes(x = run_number, y = IncorrGo, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Base Scan \nRaw Data, All Participants')
incorrGo_end <- ggplot(subset(clean_df_gng, run_number %in% c('run3', 'run4'))) +
    aes(x = run_number, y = IncorrGo, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During End Scan \nRaw Data, All Participants')

incorrNoGo_base <- ggplot(subset(clean_df_gng, run_number %in% c('run1', 'run2'))) +
    aes(x = run_number, y = IncorrNoGo, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect No Go Count During Base Scan \nRaw Data, All Participants')
incorrNoGo_end <- ggplot(subset(clean_df_gng, run_number %in% c('run3', 'run4'))) +
    aes(x = run_number, y = IncorrNoGo, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During End Scan \nRaw Data, All Participants')

incorrGo_byBlock_run1 <- ggplot(subset(clean_df_blocks, run_number %in% c('run1'))) +
    aes(x = block, y = value, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Each Block \nRun 1, All Participants')
incorrGo_byBlock_run2 <- ggplot(subset(clean_df_blocks, run_number %in% c('run2'))) +
    aes(x = block, y = value, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Each Block \nRun 2, All Participants')
incorrGo_byBlock_run3 <- ggplot(subset(clean_df_blocks, run_number %in% c('run3'))) +
    aes(x = block, y = value, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Each Block \nRun 3, All Participants')
incorrGo_byBlock_run4 <- ggplot(subset(clean_df_blocks, run_number %in% c('run4'))) +
    aes(x = block, y = value, label = ID) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle('Incorrect Go Count During Each Block \nRun 4, All Participants')

```
```{r, echo = FALSE}
grid.arrange(incorrGo_base, incorrGo_end, ncol = 2)
grid.arrange(incorrNoGo_base, incorrNoGo_end, ncol = 2)
grid.arrange(incorrGo_byBlock_run1, incorrGo_byBlock_run2, ncol = 2) 
grid.arrange(incorrGo_byBlock_run3, incorrGo_byBlock_run4, ncol = 2)
```

# Who was left out
```{r, echo = FALSE}
# Look at which participants had runs removed & how many
compare_gng_dfs <- summary(arsenal::compare(df_gng, clean_df_gng))
gng_diffs <- compare_gng_dfs[["diffs.table"]][["row.x"]]
outlierCount_gng <- as.data.frame(table(df_gng[gng_diffs,]$ID))
colnames(outlierCount_gng) <- c("ID", "outlierCount_gng")

# create new "outliers3" vector
outlierLogical_gng <- row.names(clean_df_gng) %in% gng_diffs
```
```{r, echo = FALSE}
df_omitted_runs <- cbind(clean_df_gng, outlierLogical_gng)
df_omitted_runs_all <- filter(df_omitted_runs, outlierLogical_gng == TRUE)
df_omitted_runs_all <- sort(df_omitted_runs_all[,c(1,3)])
kable(df_omitted_runs_all, caption = "Full list of runs to omit from analysis", row.names = FALSE)
```
