---
title: 'SEM Project: Latent Growth Curve Modeling of REV Training Data'
author: "Krista DeStasio"
date: "11/16/2017"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
  word_document:
    toc: no
---

```{r setup, include=FALSE}
rm(list = ls())
setwd("~/Desktop/REV_scripts/behavioral/REV_SST/scripts/analyses/")

## Install and load required packages
list.of.packages <- c("lavaan", "tidyverse", "psych")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])] 
if(length(new.packages)) install.packages(new.packages) 
lapply(list.of.packages, library, character.only = TRUE)

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, include = TRUE)
```

```{r read in data and create the data frame}
load("~/Desktop/REV_scripts/behavioral/REV_SST/scripts/analyses/df_SSRT.Rda")
load("~/Desktop/REV_scripts/behavioral/surveys/ACES.Rda")

# Merge the ACES and SSRT data frames
colnames(ACES) <- c("ID", "ACES")
ACES$ID <- as.integer(ACES$ID)
ACES$ID <- as.factor(ACES$ID)
df_ssrt <- merge(df_SSRTallSubs, ACES, by = "ID")

# Keep only the training group for these analyses
df_ssrt <- subset(df_ssrt, condition == "train")


# remove the separate ACES and SSRT data frames
rm(df_SSRTallSubs, ACES)

# Combine time and prepost and remove the not averaged SSRTs from run1, & 2, and remove the post session data
df_ssrt$time <- factor(df_ssrt$time, 
       levels = c("run1",  "run2",  "run3",  "run4",  "run5",  "run6",  "run7",  "run8",  "run9",  "run10", "run11", "run12", "run13", "run14"), 
       labels = c("pre_avg",  "remove1",  "t3",  "t4",  "t5",  "t6",  "t7",  "t8",  "t9",  "t10", "t11", "t12", "remove2", "remove3") )

df_ssrt <- subset(df_ssrt, time != "remove1" & 
                    time !="remove2" & 
                    time !="remove3" & ID != '143')

# Replace the pre_avg and post_avg SSRT with the avg SSRT
df_ssrt$SSRT <- ifelse(df_ssrt$time %in% c("pre_avg"), 
                       df_ssrt$SSRT_avg, 
                       df_ssrt$SSRT)

# Keep only the columns of interest for our analyses
df_ssrt <- df_ssrt[,c(1, 4:5, 10)]

# Replace NaN with NA
df_ssrt[ is.na(df_ssrt) ] <- NA

# Rename columns
colnames(df_ssrt) <- c("id", "time", "ssrt", "aces")

# Re-level the time and ID factors
df_ssrt$time <- factor(df_ssrt$time, 
       levels = c("pre_avg",  "t3",  "t4",  "t5",  "t6",  "t7",  "t8",  "t9",  "t10", "t11", "t12"))
df_ssrt$id <- factor(df_ssrt$id,
                     levels = levels(droplevels(df_ssrt$id)))
```

# Plots
```{r examine data for normality}
plot(ssrt ~ time, data=df_ssrt, main="SSRT x Time")

# Examine the residuals 
fit = lm(ssrt ~ aces, df_ssrt) # Run a regression analysis
plot(fit)
```

```{r Plot means}
# Means
mean.ssrt <- tapply(df_ssrt$ssrt, df_ssrt$time, FUN = mean, na.rm = T)
ssrt_data <- data.frame(ssrt = mean.ssrt, time = 0:10)
plot(mean.ssrt ~ time, ssrt_data, type = "b", xlab = "Time", ylab = "Reaction Time (Mean)")
```

````{r Slopes}
p <- ggplot(data=subset(df_ssrt, (df_ssrt$time != "pre_avg")), aes(x=time, ssrt)) 

# Line plot
p +
    geom_line(aes(group=id, color = factor(id))) + facet_wrap(~id)

# One plot
p +
    geom_smooth(aes(group=id, color = factor(id)),method=loess,se=F)+
    theme(panel.background=element_rect(fill='white'))
```

```{r make data wide for lavaan}
df_ssrt <- df_ssrt %>% 
  gather(ssrt, score, -aces, -id, -time) %>% 
  unite(variable, ssrt, time) %>% 
  spread(variable, score)
```

```{r Keep only participants with at least one training ssrt}
df_ssrt <- subset(df_ssrt, !is.na(df_ssrt$ssrt_t3) | !is.na(df_ssrt$ssrt_t4))
```

# Descriptives
```{r data normality}
describe(df_ssrt)
```

# Models
## No predictors
### Basic change model


```{r Basic change model}
# Variances allowed to differ
model_basic <- '
# Fixed coeficcients
    intercept =~ 1*ssrt_t3 + 
              1*ssrt_t4 + 
              1*ssrt_t5 + 
              1*ssrt_t6 + 
              1*ssrt_t7 + 
              1*ssrt_t8 + 
              1*ssrt_t9 + 
              1*ssrt_t10 + 
              1*ssrt_t11 + 
              1*ssrt_t12
    slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              ssrt_t5 + 
              ssrt_t6 + 
              ssrt_t7 + 
              ssrt_t8 + 
              ssrt_t9 + 
              ssrt_t10 + 
              ssrt_t11 + 
              ssrt_t12
'
modelbasic_fit <- growth(model_basic,
                     missing = "ml",
                     data = df_ssrt)

summary(modelbasic_fit)
fitmeasures(modelbasic_fit)
```

### Linear model
```{r simple linear model no predictors}
# Linear time without any predictors
model_linear <- '
# Fixed coeficcients
    intercept =~ 1*ssrt_t3 + 
              1*ssrt_t4 + 
              1*ssrt_t5 + 
              1*ssrt_t6 + 
              1*ssrt_t7 + 
              1*ssrt_t8 + 
              1*ssrt_t9 + 
              1*ssrt_t10 + 
              1*ssrt_t11 + 
              1*ssrt_t12
    linear_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              2*ssrt_t5 + 
              3*ssrt_t6 + 
              4*ssrt_t7 + 
              5*ssrt_t8 + 
              6*ssrt_t9 + 
              7*ssrt_t10 + 
              8*ssrt_t11 + 
              9*ssrt_t12
'
modellinear_fit <- growth(model_linear,
                     missing = "ml",
                     data = df_ssrt)

summary(modellinear_fit)
fitmeasures(modellinear_fit)
```

### Model comparison basic v. linear
```{r model comparison basic and linear}
(modcompbase <- anova(modelbasic_fit, modellinear_fit))
```

### Quadratic model 

The model with linear and quadratic slope components fits the data significantly better than a saturated model
```{r Quadratic model no predictors}
# ssrt model: Quadratic on time
model_quad <- '
# Fixed coeficcients
      intercept =~ 1*ssrt_t3 + 
              1*ssrt_t4 + 
              1*ssrt_t5 + 
              1*ssrt_t6 + 
              1*ssrt_t7 + 
              1*ssrt_t8 + 
              1*ssrt_t9 + 
              1*ssrt_t10 + 
              1*ssrt_t11 + 
              1*ssrt_t12
    linear_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              2*ssrt_t5 + 
              3*ssrt_t6 + 
              4*ssrt_t7 + 
              5*ssrt_t8 + 
              6*ssrt_t9 + 
              7*ssrt_t10 + 
              8*ssrt_t11 + 
              9*ssrt_t12
    quadratic_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              4*ssrt_t5 + 
              9*ssrt_t6 + 
              16*ssrt_t7 + 
              25*ssrt_t8 + 
              36*ssrt_t9 + 
              49*ssrt_t10 + 
              64*ssrt_t11 + 
              81*ssrt_t12
'

modelquad_fit <- growth(model_quad, 
                     missing = "ml", 
                     data = df_ssrt) 

summary(modelquad_fit)
fitmeasures(modelquad_fit)
```

### Model comparison, basic, linear, and quadratic
```{r model comparison shape}
(modcomp1 <- anova(modelbasic_fit, modellinear_fit, modelquad_fit))
```

## Cubic model
```{r Cubic model no predictors}
# ssrt model: Cubic on time
model_cubic <- '
# Fixed coeficcients
      intercept =~ 1*ssrt_t3 + 
              1*ssrt_t4 + 
              1*ssrt_t5 + 
              1*ssrt_t6 + 
              1*ssrt_t7 + 
              1*ssrt_t8 + 
              1*ssrt_t9 + 
              1*ssrt_t10 + 
              1*ssrt_t11 + 
              1*ssrt_t12
    linear_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              2*ssrt_t5 + 
              3*ssrt_t6 + 
              4*ssrt_t7 + 
              5*ssrt_t8 + 
              6*ssrt_t9 + 
              7*ssrt_t10 + 
              8*ssrt_t11 + 
              9*ssrt_t12
    cubic_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              8*ssrt_t5 + 
              27*ssrt_t6 + 
              64*ssrt_t7 + 
              125*ssrt_t8 + 
              216*ssrt_t9 + 
              343*ssrt_t10 + 
              512*ssrt_t11 + 
              729*ssrt_t12
'

modelcubic_fit <- growth(model_cubic, 
                     missing = "ml", 
                     data = df_ssrt) 

summary(modelcubic_fit)
fitmeasures(modelcubic_fit)
```

### Model comparison, basic, linear, quadratic, cubic
```{r model comparison through cubic}
anova(modelbasic_fit, modellinear_fit, modelquad_fit, modelcubic_fit)
```

### Conclusion

The linear model is a worse fit than the all other models based on the chi square difference test and AIC. The quadratic model fits better based on the AIC, though the chi square difference test is agnostic. 

# Model with predictors
## Quadratic slope with scan SSRT as predictor
```{r linear with scan}
# Linear time with scan as predictor
model_linearscan <- '
# Fixed coeficcients
      intercept =~ 1*ssrt_t3 + 
              1*ssrt_t4 + 
              1*ssrt_t5 + 
              1*ssrt_t6 + 
              1*ssrt_t7 + 
              1*ssrt_t8 + 
              1*ssrt_t9 + 
              1*ssrt_t10 + 
              1*ssrt_t11 + 
              1*ssrt_t12
    linear_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              2*ssrt_t5 + 
              3*ssrt_t6 + 
              4*ssrt_t7 + 
              5*ssrt_t8 + 
              6*ssrt_t9 + 
              7*ssrt_t10 + 
              8*ssrt_t11 + 
              9*ssrt_t12
quadratic_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              4*ssrt_t5 + 
              9*ssrt_t6 + 
              16*ssrt_t7 + 
              25*ssrt_t8 + 
              36*ssrt_t9 + 
              49*ssrt_t10 + 
              64*ssrt_t11 + 
              81*ssrt_t12
# Regressions
    intercept + linear_slope + quadratic_slope ~ ssrt_pre_avg
'

modelscan_fit <- growth(model_linearscan, 
                     missing = "ml", 
                     data = df_ssrt) 

summary(modelscan_fit)
fitmeasures(modelscan_fit)
```

### Model comparison with and without scan as predictor
```{r scan as predictor}
anova(modelquad_fit, modelscan_fit)
```

## Quadratic slope with early adversity as predictor
```{r EA as predictor}
# Linear time with early adversity as predictor
model_linearaces <- '
# Fixed coeficcients
      intercept =~ 1*ssrt_t3 + 
              1*ssrt_t4 + 
              1*ssrt_t5 + 
              1*ssrt_t6 + 
              1*ssrt_t7 + 
              1*ssrt_t8 + 
              1*ssrt_t9 + 
              1*ssrt_t10 + 
              1*ssrt_t11 + 
              1*ssrt_t12
    linear_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              2*ssrt_t5 + 
              3*ssrt_t6 + 
              4*ssrt_t7 + 
              5*ssrt_t8 + 
              6*ssrt_t9 + 
              7*ssrt_t10 + 
              8*ssrt_t11 + 
              9*ssrt_t12
quadratic_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              4*ssrt_t5 + 
              9*ssrt_t6 + 
              16*ssrt_t7 + 
              25*ssrt_t8 + 
              36*ssrt_t9 + 
              49*ssrt_t10 + 
              64*ssrt_t11 + 
              81*ssrt_t12
# Regressions
    intercept + linear_slope + quadratic_slope ~ aces
'

modelaces_fit <- growth(model_linearaces, 
                     missing = "ml", 
                     data = df_ssrt) 

summary(modelaces_fit)
fitmeasures(modelaces_fit)
```

### Model comparison with and without EA as predictor
```{r model comparison aces}
anova(modelquad_fit, modelaces_fit)
```

```{r EA and scan as predictors, eval=FALSE}
## Quadratic slope with scan SSRT and EA as predictors
# Linear time with early adversity as predictor
model_linearboth <- '
# Fixed coeficcients
      intercept =~ 1*ssrt_t3 + 
              1*ssrt_t4 + 
              1*ssrt_t5 + 
              1*ssrt_t6 + 
              1*ssrt_t7 + 
              1*ssrt_t8 + 
              1*ssrt_t9 + 
              1*ssrt_t10 + 
              1*ssrt_t11 + 
              1*ssrt_t12
    linear_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              2*ssrt_t5 + 
              3*ssrt_t6 + 
              4*ssrt_t7 + 
              5*ssrt_t8 + 
              6*ssrt_t9 + 
              7*ssrt_t10 + 
              8*ssrt_t11 + 
              9*ssrt_t12
quadratic_slope =~  0*ssrt_t3 + 
              1*ssrt_t4 + 
              4*ssrt_t5 + 
              9*ssrt_t6 + 
              16*ssrt_t7 + 
              25*ssrt_t8 + 
              36*ssrt_t9 + 
              49*ssrt_t10 + 
              64*ssrt_t11 + 
              81*ssrt_t12
# Regressions
   intercept + linear_slope + quadratic_slope ~ aces + ssrt_pre_avg
'

modelboth_fit <- growth(model_linearboth, 
                     missing = "ml", 
                     data = df_ssrt)

summary(modelboth_fit)
fitmeasures(modelboth_fit)
```


```{r model comparison predictors, eval=FALSE}
anova(modelscan_fit, modelaces_fit, modelboth_fit, modelquad_fit)
```

## Conclusions
Inclusion of scores on the early adversity questionare as a predictor does not significantly improve model fit. Nor does inclusion of scan sst scores as a predictor improve model fit over the quadratic model. 

# What does the final model look like?
```{r Draw the model}
semPlot::semPaths(modelquad_fit)
```
