---
title: 'REV Behavioral Data Analysis: SST'
author: "Krista DeStasio"
date: "4/26/2017"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
## R version 3.4.3 ##
rm(list = ls())
setwd("~/Desktop/REV_scripts/behavioral/REV_SST/scripts/analyses/")

## Install and load required packages
list_of_packages <- c("stringr", "tidyverse", "reshape2", "ggplot2", "psych", "gridExtra", "knitr", "lme4", "memisc", "withr", "ez")
new_packages <- list_of_packages[!(list_of_packages %in% installed.packages()[,"Package"])] 
if (length(new_packages)) install.packages(new_packages, repos = "http://cran.us.r-project.org")
lapply(list_of_packages, library, character.only = TRUE)
rm(list = ls(pattern = "packages"))

knitr::opts_chunk$set(fig.width = 12, fig.height = 8, fig.path = 'Figs/', echo = FALSE, warning = FALSE, message = FALSE)
```

### Key:

**Key to Stop-signal task components:**  

**SSD** -- Stop-signal delay -- _Time from go stimulus to stop signal_  
**RT** -- Reaction time -- _Time from go stimulus to button press_  
**ssrt** -- Stop-signal response time -- _ssrt = (nth RT - mean SSD)_    
**Signal-inhibit trial** -- response witheld on a stop-signal trial -- _RT > (ssrt + SSD)_  
**Signal-respond trial** -- erroneous response on a stop-signal trial -- _RT < (ssrt + SSD)_  

### Note:  
Results calculated based on the inegration method of estimating the stop-signal response time (ssrt). This method helps to account for skewness of the RT distribution and anticipatory slowing in advance of the stop stignal. As recommended in:  

>Verbruggen, F., Chambers, C. D., & Logan, G. D. (2013). Fictitious inhibitory differences: how skewness and slowing distort the estimation of stopping latencies. _Psychological Science, 24(3)_, 352–62. https://doi.org/10.1177/0956797612457390  

The integration method finds "the point at which the integral equals equals the probability of responding, $p(respond|signal)$, for a specific delay." 

```{r Create the participant ID and condition variables}
id <- as.factor(c(1:144)) # Create the subject ID column
condition <- c(0, 1, 0, 0, 0, 1, 1, 0, 1, 0, 0, 1, 1, 1, 1, 1, 0, 0, 1, 0, 1, 1, 1, 0, 1, 1, 0, 0, 0, 1, 1, 1, 1, 0, 1, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 1, 0, 1, 0, 1, 1, 0, 0, 0, 1, 1, 1, 0, 1, 0, 1, 1, 1, 0, 0, 0, 0, 0, 1, 0, 0, 1, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 1, 1, 0, 1, 1, 0, 1, 0, 1, 1, 1, 1, 0, 0, 1, 1, 1, 1, 1, 0, 0, 1, 1, 1, 1, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 1, 0, 1, 1, 0, 0, 1, 0, 1, 1, 0, 1, 1, 1, 0, 0, 1, 0) # Match the participant to their condition
condition <- factor(condition, labels = c("control", "train"))
```

```{r Import task data}
## Import the ssrt results output from the extractAllSSTResults.m script
ssrt_data <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/singleVarTxts/REV_ssrtint16.txt",
  sep = "\t", header = FALSE)
## Percent inhibition
pct_inhibition <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/singleVarTxts/REV_PctInhib16.txt",
  sep = "\t", header = FALSE)
## No Response Counts
count_noresponse <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/initialCheck/NRCount.txt",
  sep = "\t", header = FALSE)
## Wrong Go Counts
count_wrong_go <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/initialCheck/wrongGoCount.txt",
  sep = "\t", header = FALSE)
```

```{r Put all data frames in long form}
# Make a vector containing all the dataframes
dfs <- c("count_noresponse", "count_wrong_go", "pct_inhibition", "ssrt_data") 
runs <- c("run1", "run2","run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12", "run13", "run14")

# Name the columns for each data frame by the run number
for (df in dfs) {
  df_tmp <- get(df)
  names(df_tmp) <- runs
  assign(df, df_tmp)
}

# Append the participant IDs and conditions to the front of each data frame
for (df in dfs) {
    df_tmp <- get(df)
    df_tmp <- cbind(id, condition, df_tmp)
    assign(df, df_tmp)
}

# Put the data frames in long form and append "_long" to the data frame name
for (df in dfs) {
    df_tmp <- get(df)
    df_tmp <- melt(data = df_tmp, 
                   idvars = id, 
                   measure.vars = runs, 
                   variable.name = "session_number", 
                   value.name = df)
    assign(paste(df, "_long", sep = ""),df_tmp)
}

# Clean up the workspace
rm(df_tmp)
rm(list = dfs)
```

```{r Create a single data frame}
df_ssrt_rawscores <- cbind(ssrt_data_long, count_noresponse_long[,4], count_wrong_go_long[,4], pct_inhibition_long[,4])
colnames(df_ssrt_rawscores) <- c("id", "condition", "session_number", "ssrt", "count_noresponse", "count_wrong_go", "pct_inhibition")

# Clean up the workspace
#rm(list = c("ssrt_data_long", "count_noresponse_long", "count_wrong_go_long", "pct_inhibition_long"))
rm(list = ls(pattern = "_long"))
# Replace NaNs with Na
df_ssrt_rawscores[ is.na(df_ssrt_rawscores) ] <- NA
```

# Visualizing Participant Responses
Looking for: slow reaction times, lots of no responses, and weird (negative, super small, super big) ssrts

## Cut-offs
Cut-off values are determined by visual inspection of the scatterplots, which are presented below in raw and trimmed form.  

- Non-Responses  
    + During Training: upper limit 25  
    + During Scans: upper limit 50  
- Wrong Go Count   
    + During Training (training group only): upper limit 25  
    + During Scans: upper limit 25   
- Percent inhibition
    + During Scans: lower limit 15, upper limit 75
    + During Training (training group only): lower limit 15, upper limit 75
- ssrts
    + During Training: upper limit 500
    + During Scanning: upper limit 850, lower limit 100


```{r runs omitted pct inhibition}
### PERCENT INHIBITION ###
## Replace ssrts with NAs if percent inihibition is  > 75 | < 15 during training (training group only) or > 75 | < 20 during scans (all participants)
df_ssrt <- df_ssrt_rawscores %>% 
    mutate(ssrt = replace(ssrt, 
                         which(pct_inhibition > 75 & 
                                   condition == "train" & 
                                   session_number != "run1" & session_number != "run2" & session_number != "run13" & session_number != "run14" | pct_inhibition < 15 & condition == "train" & session_number != "run1" & session_number != "run2" & session_number != "run13" & session_number != "run14") , NA)) 
# Training
df_ssrt <- df_ssrt %>% 
    mutate(ssrt = replace(ssrt, 
                         which(pct_inhibition > 75 & session_number != "run3" & session_number != "run4" & session_number != "run5" & session_number != "run6" & session_number != "run7" & session_number != "run8" & session_number != "run9" & session_number != "run10" & session_number != "run11" & session_number != "run12" | pct_inhibition < 20 & session_number != "run3" & session_number != "run4" & session_number != "run5" & session_number != "run6" & session_number != "run7" & session_number != "run8" & session_number != "run9" & session_number != "run10" & session_number != "run11" & session_number != "run12"), NA)) # Scans

## Replace the percent inhibition with NAs if they are > 75 | < 15 during training (training group only) or > 75 | < 20 during scans (all participants)
df_ssrt <- df_ssrt %>% 
    mutate(pct_inhibition = replace(pct_inhibition, 
                                  which(pct_inhibition < 15  & condition == "train" & session_number != "run1" & session_number != "run2" & session_number != "run13" & session_number != "run14" | pct_inhibition > 75 & condition == "train" & session_number != "run1" & session_number != "run2" & session_number != "run13" & session_number != "run14" ), NA)) # Training

df_ssrt <- df_ssrt %>% 
    mutate(pct_inhibition = replace(pct_inhibition, 
                                  which(pct_inhibition < 15  & session_number != "run3" & session_number != "run4" & session_number != "run5" & session_number != "run6" & session_number != "run7" & session_number != "run8" & session_number != "run9" & session_number != "run10" & session_number != "run11" & session_number != "run12" | pct_inhibition > 75 & session_number != "run3" & session_number != "run4" & session_number != "run5" & session_number != "run6" & session_number != "run7" & session_number != "run8" & session_number != "run9" & session_number != "run10" & session_number != "run11" & session_number != "run12"), NA)) # Scans

# Look at which participants had runs removed & how many
outliers <- (!df_ssrt_rawscores$ssrt %in% df_ssrt$ssrt)
outliers_pct_inhibition <- as.data.frame(table(df_ssrt_rawscores[outliers,]$id))
colnames(outliers_pct_inhibition) <- c("id", "runs_omitted_pct_inhibition")
```

```{r Remove problem runs no-response}
### NO RESPONSE ###
## Replace the ssrts with NAs if no-responses are > 25 during training or > 50 during scans
df_ssrt <- df_ssrt %>% 
    mutate(ssrt = replace(ssrt, 
                         which(count_noresponse > 25 & session_number != "run1" & session_number != "run2" & session_number != "run13" & session_number != "run14" ), NA)) # Training

df_ssrt <- df_ssrt %>% 
    mutate(ssrt = replace(ssrt, 
                         which(count_noresponse > 50), NA)) # Scans

## Replace the no-responses with NAs if they are > 25 during training or > 50 during scans
df_ssrt <- df_ssrt %>% 
    mutate(count_noresponse = replace(count_noresponse, 
                                  which(count_noresponse > 25 & session_number != "run1" & session_number != "run2" & session_number != "run13" & session_number != "run14" ), NA)) # Training

df_ssrt <- df_ssrt %>% 
    mutate(count_noresponse = replace(count_noresponse, 
                                  which(count_noresponse > 50), NA)) # Scans

# Look at which participants had runs removed & how many
outliers <- (!df_ssrt_rawscores$ssrt %in% df_ssrt$ssrt)
outliers_noresponse <- as.data.frame(table(df_ssrt_rawscores[outliers,]$id))
colnames(outliers_noresponse) <- c("id", "runs_omitted_noresponse")
```

```{r Remove problem runs wrong no-gos}
### WRONG GO ###
## Replace the ssrts with NAs if wrong-gos are > 25 during training (training group only) or > 25 during scans (all participants)
df_ssrt <- df_ssrt %>% 
    mutate(ssrt = replace(ssrt, 
                            which(condition == "train" & count_wrong_go > 25 & session_number != "run1" & session_number != "run2" & session_number != "run13" & session_number != "run14"), NA)) # Training

df_ssrt <- df_ssrt %>% 
    mutate(ssrt = replace(ssrt, 
                           which(count_wrong_go > 25 & session_number != "run3" & session_number != "run4" & session_number != "run5" & session_number != "run6" & session_number != "run7" & session_number != "run8" & session_number != "run9" & session_number != "run10" & session_number != "run11" & session_number != "run12"), NA)) # Scans

## Replace the wrong-gos with NAs if they are > 25 during training (training group only) or > 25 during scans (all participants)
df_ssrt <- df_ssrt %>% 
    mutate(count_wrong_go = replace(count_wrong_go, 
                        which(condition == "train" & count_wrong_go > 25 & session_number != "run1" & session_number != "run2" & session_number != "run13" & session_number != "run14"), NA)) # Training

df_ssrt <- df_ssrt %>% 
    mutate(count_wrong_go = replace(count_wrong_go, 
                        which(count_wrong_go > 25 & session_number != "run3" & session_number != "run4" & session_number != "run5" & session_number != "run6" & session_number != "run7" & session_number != "run8" & session_number != "run9" & session_number != "run10" & session_number != "run11" & session_number != "run12"), NA)) # Scan

# Look at which participants had runs removed & how many
outliers <- (!df_ssrt_rawscores$ssrt %in% df_ssrt$ssrt)
outliers_wrong_go <- as.data.frame(table(df_ssrt_rawscores[outliers,]$id))
colnames(outliers_wrong_go) <- c("id", "runs_omitted_wrong_go")
```

```{r runs omitted ssrt}
### ssrt ###
## Replace the ssrts with NAs if they are > 500 during training (training group only) or > 850 | < 100 during scans (all participants)
df_ssrt <- df_ssrt %>% 
    mutate(ssrt = replace(ssrt, 
                         which(ssrt > 500 & condition == "train" & session_number != "run1" & session_number != "run2" & session_number != "run13" & session_number != "run14"), NA)) # Training

df_ssrt <- df_ssrt %>% 
    mutate(ssrt = replace(ssrt,
                         which(ssrt > 850 & session_number != "run3" & session_number != "run4" & session_number != "run5" & session_number != "run6" & session_number != "run7" & session_number != "run8" & session_number != "run9" & session_number != "run10" & session_number != "run11" & session_number != "run12" | ssrt < 100 & session_number != "run3" & session_number != "run4" & session_number != "run5" & session_number != "run6" & session_number != "run7" & session_number != "run8" & session_number != "run9" & session_number != "run10" & session_number != "run11" & session_number != "run12"), NA)) # Scans

# Look at which participants had runs removed & how many
outliers <- (!df_ssrt_rawscores$ssrt %in% df_ssrt$ssrt)
outliers_ssrt <- as.data.frame(table(df_ssrt_rawscores[outliers,]$id))
colnames(outliers_ssrt) <- c("id", "runs_omitted_ssrt")
```

## View omitted runs
```{r Create a table of omitted runs}
# See omitted
dfs <- list(outliers_pct_inhibition, outliers_noresponse, outliers_wrong_go, outliers_ssrt)
outliers_tableFull <- plyr::join_all(dfs, by = "id")
outliers_table <- outliers_tableFull[which(outliers_tableFull$runs_omitted_ssrt != 0),]
kable(outliers_table, caption = "Runs Omitted (columns are cumulative)")
summary(outliers_tableFull$runs_omitted_ssrt)

# Cleanup
rm(dfs)
rm(list = ls(pattern = "outliers_"))
```

## Notes on problem runs

- 134 - kept switching correct/incorrect direction presses.  
- 82 - switched buttons 1/2 way through run 7.  
- 91 - stopped trying for last part of run 3. Repeatedly pressing same key (not an assigned key).  
- 26 - Participant in experimental condition, but has 0% inhibition during all training runs.  
- 51 - Why doesn't 51 have the base scan ssrts?   
    + Can't be calculated due to high number of non-responses and wrong-gos.  
- 138 - Why doesn't 138 have the base scan ssrts?   
    + Can't be calculated due to high number of wrong-gos.  

## Comparison Plots: Raw vs. Cleaned Data  
```{r Create plots of the data}
training_runs = c("run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12")
scanning_runs = c("run1", "run2", "run13", "run14")
geom_text_layer <- geom_text(aes(label = ifelse(count_noresponse > 10,as.character(id),'')),hjust = 0, vjust = 0, na.rm = TRUE)

### CHECKING FOR PROBLEMS ###
## Plot All Non-responses
plot_noResp_raw <- ggplot(df_ssrt_rawscores, aes(x = session_number, y = count_noresponse, label = id)) +
    geom_point(na.rm = TRUE) +
     geom_text_layer +
    ggtitle("Num of Non-Responses Raw Data, \nAll Participants, All Time Points")

## Plot Wrong Go Count, Scans, All Participants
plot_wrongGo_rawAll <- ggplot(subset(df_ssrt_rawscores, session_number %in% scanning_runs)) +
    aes(x = session_number, y = count_wrong_go, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text_layer +
    ggtitle("Wrong Go Count During Scans \nRaw Data, All Participants")

## Plot Wrong Gos During Training, Training Group Only
plot_wrongGo_rawTrn <- ggplot(subset(df_ssrt_rawscores,session_number %in%  training_runs & condition == "train")) +
    aes(x = session_number, y = count_wrong_go, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = ifelse(count_wrong_go > 25,as.character(id),'')),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle("Wrong Go Count During Training \nRaw Data, Training Group Only")

## Plot ssrts during Scan
plot_ssrt_rawScan <- ggplot(subset(df_ssrt_rawscores,session_number %in% scanning_runs)) +
    aes(x = session_number, y = ssrt, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text_layer +
    ggtitle("ssrts During Scans, \nAll Participants")

## Plot ssrts during training, only for the training group
plot_ssrt_rawTrn <- ggplot(subset(df_ssrt_rawscores, session_number %in% training_runs & condition == "train")) +
    aes(x = session_number, y = ssrt, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text_layer +
    ggtitle("ssrts During Training Raw Data, \nTraining Group Only")

## Plot Pct inhibition during Scan
plot_PctInhib_rawScan <- ggplot(subset(df_ssrt_rawscores,session_number %in% scanning_runs)) +
    aes(x = session_number, y = pct_inhibition, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text_layer +
    ggtitle("Percent Inhibition During Scans, \nAll Participants")

## Plot Percent Inhibition during training for the training group 
plot_pctInhib_rawTrn <- ggplot(subset(df_ssrt_rawscores, session_number %in% training_runs & condition == "train")) +
    aes(x = session_number, y = pct_inhibition, label = id) +
    geom_point(na.rm = TRUE) +
    geom_jitter(width = 0.25) +
    geom_text_layer +
    ggtitle("Percent Inhibition Raw Data, \nTraining Group During Training")

### CLEANED DATA ###

## Plot All Non-responses
plot_noResp_clean <- ggplot(df_ssrt, aes(x = session_number, y = count_noresponse, label = id)) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = ifelse(count_noresponse > 10,as.character(id),'')),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle("Non-Responses, All P's, All Times, \nUpper Limits: Training 25, Scans 50")

## Plot Wrong Go Count, Scans, All Participants
plot_wrongGo_cleanAll <- ggplot(subset(df_ssrt, session_number %in% scanning_runs)) +
    aes(x = session_number, y = count_wrong_go, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text_layer +
    ggtitle("Wrong Gos During Scans, All P's, \nUpper Limit Cut-Off of 25")

## Plot Wrong Gos During Training, Training Group Only
plot_wrongGo_cleanTrn <- ggplot(subset(df_ssrt,session_number %in%  training_runs & condition == "train")) +
    aes(x = session_number, y = count_wrong_go, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = ifelse(count_wrong_go > 25,as.character(id),'')),hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle("Wrong Go's During Training, \nTraining Group Only, Upper Limit 25")

## Plot Pct Inhibition during training, training group only 
plot_PctInhib_cleanTrn <- ggplot(subset(df_ssrt, session_number %in%  training_runs & condition == "train")) +
    aes(x = session_number, y = pct_inhibition, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text(aes(label = as.character(id)), hjust = 0, vjust = 0, na.rm = TRUE) +
    ggtitle("Percent Inhibition During Training, \nTraining Group Only, Lower Limit 15, Upper Limit 75")

## Plot pct inhib during scans for all participants
plot_PctInhib_cleanScan <- ggplot(subset(df_ssrt,session_number %in% scanning_runs)) +
    aes(x = session_number, y = pct_inhibition, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text_layer +
    ggtitle("Pct Inhibition During Scans, All P's, \n Lower Limit 15, Upper Limit 75")

## Plot ssrts during Scan
plot_ssrt_cleanScan <- ggplot(subset(df_ssrt,session_number %in% scanning_runs)) +
    aes(x = session_number, y = ssrt, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text_layer +
    ggtitle("ssrts During Scans, All P's, \nUpper Limit 850, Lower Limit 100")

## Plot ssrts during training, only for the training group
plot_ssrt_cleanTrn <- ggplot(subset(df_ssrt, session_number %in%  training_runs & condition == "train")) +
    aes(x = session_number, y = ssrt, label = id) +
    geom_point(na.rm = TRUE) +
    geom_text_layer +
    ggtitle("ssrts During Training, \nTraining Group, Upper Limit 500")

```

### Wrong Gos  

```{r Plot wrong-gos}
# Define grid layout to locate plots and print each graph
grid.arrange(plot_wrongGo_rawAll, plot_wrongGo_cleanAll, ncol = 2)
grid.arrange(plot_wrongGo_rawTrn, plot_wrongGo_cleanTrn, ncol = 2)
```

### Non-Responses
```{r Plot non-responses}
grid.arrange(plot_noResp_raw, plot_noResp_clean, ncol = 2)
```

### Percent Inhibition
```{r Plot percent inhibition}
grid.arrange(plot_PctInhib_rawScan,plot_PctInhib_cleanScan, ncol = 2)
grid.arrange(plot_pctInhib_rawTrn, plot_PctInhib_cleanTrn, ncol = 2)
```

### ssrts
```{r plot ssrts}
grid.arrange(plot_ssrt_rawScan, plot_ssrt_cleanScan, ncol = 2)
grid.arrange(plot_ssrt_rawTrn, plot_ssrt_cleanTrn, ncol = 2)
```

```{r cleanup environment after plots}
rm(list = ls(pattern = "plot_"))
```

## Description of Omitted Runs by Participant
```{r Compare clean and raw data}
## Compare raw and cleaned data frames to find how many runs dropped by participant. Get avg. dropped, min, max, and outliers.
omitted_runs <- (!df_ssrt_rawscores$ssrt %in% df_ssrt$ssrt)

# Plot the number of omitted runs by participant ID
ggplot(df_ssrt_rawscores[omitted_runs,], aes(x = id)) +
    geom_bar() +
    theme(plot.title = element_text(hjust = 0.5)) +
    ggtitle("Number of Runs Omitted Per Participant") +
    labs(x = "Participant ID", y = "Number of Runs Omitted")

run_omit <- as.data.frame(table(df_ssrt_rawscores[omitted_runs,]$id))
summary(run_omit$Freq)

rm(run_omit)
```

```{r Create the Pre and Post average ssrt scores, include=FALSE}
# Make a column in the dataframe called prepost. If the run numbers are 1 or 2, put "pre" in the new column. If run num = 13 or 14, put "post" in the new column
df_ssrt$prepost <- ifelse(df_ssrt$session_number %in% 
                              c("run1", "run2"), "pre", 
                          ifelse(df_ssrt$session_number %in% 
                                     c("run13", "run14"), "post", NA))

# Take the mean of cells for which IDs match and prepost matches
df_ssrt_means <- df_ssrt %>%
    group_by(id, prepost) %>% 
    summarise(mean(ssrt, na.rm = TRUE)) 

# Keep only average values for scan sessions, discard training session averages
df_ssrt_means <- df_ssrt_means[ which(df_ssrt_means$prepost == "pre" | df_ssrt_means$prepost == "post"), ] 
df_ssrt_means$prepost <- as.factor(df_ssrt_means$prepost) # Make prepost a factor
df_ssrt_means <- df_ssrt_means[order(df_ssrt_means$prepost),] # Order values in the data frame by the prepost column

condition_twice <- cbind(rep(condition, 2))
condition_twice <- factor(condition_twice, labels = c("control", "train"))

df_ssrt_means <- merge(condition_twice, df_ssrt_means, by = 0)
df_ssrt_means <- df_ssrt_means[order(df_ssrt_means$id),2:5]
colnames(df_ssrt_means) <- c("condition", "id", "prepost", "ssrt_avg")
df_ssrt <- merge(df_ssrt, df_ssrt_means, by = c("id", "prepost", "condition"), all = TRUE)

# Replace NaNs with Na
df_ssrt[ is.na(df_ssrt) ] <- NA

rm(df_ssrt_means)
```

## Final Sample Viable Training Sessions
```{r Plot how many viable runs participants have}
# Count the viable sessions during "training" for the training group
df_viable_train <- subset(df_ssrt[ which(is.na(df_ssrt$prepost)), ], 
                          condition == "train") %>% 
    group_by(id) %>% 
    summarize(ViableN = sum(!is.na(ssrt)))

# Plot the training group
qplot_viable_train <- qplot(df_viable_train$ViableN, 
                            geom = "bar", 
                            xlab = "Viable SST Runs", 
                            ylab = "Count", 
                            main = "Viable Training Sessions, Training Group")

# Count the viable sessions during "training" for the conrol group
df_viable_control <- subset(df_ssrt[ which(is.na(df_ssrt$prepost)), ], 
                            condition == "control") %>% 
    group_by(id) %>% 
    summarize(ViableN = sum(!is.na(ssrt)))

# Plot the control group
qplot_viable_contr <- qplot(df_viable_control$ViableN, 
                            geom = "bar", xlab = 
                                "Viable SST Runs", 
                            ylab = "Count", 
                            main = "Viable Training Sessions, Control Group")

grid.arrange(qplot_viable_train, qplot_viable_contr, ncol = 2)

rm(list = ls(pattern = "qplot"))
```

**Count of viable training sessions (out of 10 possible), training group:**
```{r plot viable sessions for training group}
table(df_viable_train$ViableN)
```

**Count of viable training sessions (out of 10 possible), control group:**
```{r plot viable sessions for control group}
table(df_viable_control$ViableN)
```

**Who was excluded based on too few training sessions?**
```{r Excluded based on viable training sessions}
## Exclude participants with too few training sessions
(exclude <- as.numeric(df_viable_train$id[(df_viable_train$ViableN < 6)]))
rm(list = ls(pattern = "df_viable"))
```

```{r}
# Data frame with all runs, participants excluded based on above criteria
df_ssrt <- df_ssrt %>%
    mutate(ssrt = replace(ssrt,
                          which(id %in% exclude), NA))
df_ssrt$prepost <- as.factor(df_ssrt$prepost)
df_ssrt$prepost <- relevel(df_ssrt$prepost, ref = "pre") # make baseline the reference group
df_ssrt$id <- factor(df_ssrt$id)

# Export cleaned data frame
save(df_ssrt, file = "df_ssrt.Rda")
```

# Analyses of ssrt Data
## Pre-post change in ssrt

### Multilevel model test of primary hypothesis
```{r Model pre-post change with lmer}
# Keep only participants with base and end session data
df_ssrt_hasprepost <- df_ssrt[complete.cases(df_ssrt),]
df_ssrt_hasprepost <- unique(df_ssrt_hasprepost[,c(1:3,9)])
tt <- table(df_ssrt_hasprepost$id)
df_ssrt_hasprepost <- df_ssrt_hasprepost[df_ssrt_hasprepost$id %in% names(tt[tt > 1]), ]

# Multilevel model with intercept allowed to vary & fixed slopes for session_number & condition
multilevel_model <- lmer( ssrt_avg ~ prepost*condition + (1 |id), data = df_ssrt_hasprepost )
kable(anova(multilevel_model), digits = 2) # have to use anova table rather than summary
```

### Repeated measures ANOVA test of main hypothesis for comparison
```{r Model pre-post change with ezANOVA and lmer}
# Repeated measures ANOVA with ssrt as DV, session_number as within subs factor, and condition as between subs factor
ezmultilevel_model <- ez::ezANOVA(data = df_ssrt_hasprepost, 
                                  dv = ssrt_avg, 
                                  wid = id, 
                                  within = prepost, 
                                  between = condition, 
                                  type = 3, detailed = TRUE) 
kable(ezmultilevel_model$ANOVA, digits = 2, caption = "Change in Stop-Signal Response Time")
```

### Plots
```{r Bar plot of pre-post change in ssrt}
# calculate the means to plot
groups <- group_by(df_ssrt_hasprepost, condition, prepost)
plot_data <- dplyr::summarise(groups, 
                       mean = mean(ssrt_avg, na.rm = TRUE),
                       sd = sd(ssrt_avg, na.rm = TRUE),
                       n = n())
plot_data <- mutate(plot_data,
                    se = sd/sqrt(n),
                    ci = qt(0.975,df = n - 1)*se)

# Re-level and rename the condition factor for plotting
plot_data$condition <- factor(plot_data$condition, levels(plot_data$condition)[c(2,1)])
plot_data$condition <- plyr::revalue(plot_data$condition, c("train" = "Training", "control" = "Control"))

# Bar graph of pre-post change by condition with standard error bars.

ggplot(plot_data, aes(x = condition, y = mean, fill = interaction(prepost, condition))) +
   geom_bar(stat = "identity", position = position_dodge(), color = "black", size = .3) +
  geom_errorbar(aes(ymin = mean - ci, ymax = mean + ci), 
                size = .8,
                width = .2,
                position = position_dodge(.9)) +
    xlab("Condition") +
    ylab("ssrt (ms)") +
scale_fill_manual(values = c("#28B463", "#90EE90", "#4169E1", "#87CEEB"),name = "Time", 
              labels = c("Baseline", "Endpoint", "Baseline","Endpoint")) +
    theme(plot.title = element_text(hjust = 0.5)) +
    ggtitle("Mean Stop-Signal Reaction Time at \nPre and Post Intervention by Condition") +
    coord_cartesian(ylim = c(200, 320))  +
    scale_y_continuous(breaks = seq(200, 320, 10)) +
    theme(axis.text = element_text(size = 24),
        axis.title = element_text(size = 24, face = "bold"),
        legend.title = element_text(size = 14, face = "bold"),
        legend.position = c(.98, .98),
        legend.justification = c("right", "top"),
        legend.key.size = unit(.5, "cm"),
        legend.text = element_text(size = 14),
        title = element_text(size = 24))
```

```{r plot the model data}
ggplot(df_ssrt_hasprepost, aes(x = prepost, y = ssrt_avg, fill = condition)) +
    geom_boxplot(na.rm = TRUE) +
    theme(plot.title = element_text(hjust = 0.5)) +
    ggtitle("Pre and Post Stop Signal \nResponse Time (ssrt) by Group") + 
    labs(x = "Time Point", y = "Stop Signal Response Time") +
    scale_fill_discrete(name = "Condition",
                         breaks = c("control", "train"),
                         labels = c("Control", "Training"))
```

## Final sample 
```{r final sample description}
(table(df_ssrt_hasprepost$condition))/2
included_ids <- dimnames(table(df_ssrt_hasprepost$id))
save(included_ids, file = "Included_ids.rda")
rm(included_ids)
```

# Training sessions
## Linear effect of time within the training sessions (in the training group)
```{r Use lmer to examine training slopes}
## Create data frame of only training sessions for training group only
df_ssrttrain <- subset(df_ssrt, condition == "train" & is.na(prepost)) 
## Data frame of only training sessions, both control and training groups
df_ssrt10ses <- subset(df_ssrt, !is.na(prepost)) 

# Model
df_ssrttrain$session_number <- as.numeric(df_ssrttrain$session_number)
mlmodel <- lmer( ssrt ~ session_number + (1 + session_number|id), data = df_ssrttrain )
summary(mlmodel)

df_ssrt10ses$session_number <- as.numeric(df_ssrt10ses$session_number)
full_mlModel <- lmer( ssrt ~ condition*session_number + (1 + session_number | id), data = df_ssrt10ses)
summary(full_mlModel)
```

# Plots and summary stats of change
## Plots
```{r Boxplots of SST performance across time}
ggplot(subset(df_ssrt, condition == "train" | condition == "control" & session_number %in% c("run1", "run2", "run13", "run14"))) + 
    aes(x = session_number, y = ssrt, fill = condition) +
    geom_boxplot(na.rm = TRUE) +
    coord_flip() +
    scale_x_discrete(limits = rev(levels(df_ssrt$session_number))) +
    theme(plot.title = element_text(hjust = 0.5)) +
    ggtitle("Stop Signal Response Times \nby Time and Group") +
    labs(x = "Time Point", y = "Stop Signal Response Time") +
    scale_fill_discrete(name = "Condition",
                         breaks = c("control", "train"),
                         labels = c("Control", "Training"))
```

## Summary stats
```{r}
subjectlist_included_final_analysis <- c(044, 114, 003, 035, 090, 141, 070, 102, 052, 039, 111, 069, 097, 084, 027, 075, 011, 118, 023, 080, 065, 036, 100, 094, 010, 029, 037, 041, 074, 142, 073, 121, 021, 018, 076, 077, 031, 050, 107, 082, 056, 022, 048, 115, 006, 024, 093, 140, 131, 108, 144, 054, 104, 109, 130, 137, 129, 053, 098, 016, 046, 017, 110, 126, 135, 067, 020, 038, 127, 089, 086, 013, 001, 060, 078)
df_ssrt_final_included <- df_ssrt[which(df_ssrt$id %in% subjectlist_included_final_analysis), ]
df_ssrt_final_included <- unique(df_ssrt_final_included[!is.na(df_ssrt_final_included$prepost),])
tt <- table(df_ssrt_final_included$id)
df_ssrt_final_included <- df_ssrt_final_included[df_ssrt_final_included$id %in% names(tt[tt > 1]), ]
df_ssrt_final_included$id <- factor(df_ssrt_final_included$id)
df_ssrt_final_included$prepost <- relevel(df_ssrt_final_included$prepost, ref = "pre")
kable(aggregate(df_ssrt_final_included[, 9], list(df_ssrt_final_included$prepost), mean))
kable(aggregate(df_ssrt_final_included[, 9], list(df_ssrt_final_included$prepost, df_ssrt_final_included$condition), mean))
```

```{r}
pre <- subset(df_ssrt_final_included, prepost == 'pre')
post <- subset(df_ssrt_final_included, prepost == 'post')
par(mfrow = c(2,2))
hist(pre$ssrt_avg, xlim = c(100,500), xlab = "Mean SSRT", main = "Histogram of SSRT Averaged \nat Baseline")
hist(post$ssrt_avg, xlim = c(100,500), xlab = "Mean SSRT",  main = "Histogram of SSRT Averaged \n at Endpoint")

pre_run2 <- subset(df_ssrt_final_included, session_number == 'run2')
post_run2 <- subset(df_ssrt_final_included, session_number == 'run14')
hist(pre_run2$ssrt, xlim = c(100,500), xlab = "SSRT", main = "Histogram of SSRT During \n2nd Run at Baseline")
hist(post_run2$ssrt, xlim = c(100,500), xlab = "SSRT",  main = "Histogram of SSRT During \n2nd Run at Endpoint")
```



<!-- # Post-hoc -->
<!-- ## Partial eta-squared -->
<!-- ```{r Partial eta-squared} -->
<!-- anova_table <- anova(multilevel_model) -->
<!-- SS_interaction <- anova_table$'Sum Sq'[3] -->

<!-- mlm_summary <- summary(multilevel_model) -->
<!-- SS_error <- sum(mlm_summary$residuals^2) -->
<!-- partial_etasq <- SS_interaction / (SS_interaction + 3705.7) -->
<!-- meanSqError <- 3705.7 -->

<!-- ``` -->

<!-- ## Correlation coefficient for pre & post ssrt -->
<!-- ```{r Correlation coefficient} -->
<!-- # Create a date frame with averaged ssrt scores in separate columns for pre and post sessions -->
<!-- forCorr <- dcast(data = df_ssrt_hasprepost, formula = id ~ prepost, fun.aggregate = sum, value.var = "ssrt_avg") -->
<!-- forCorr <- forCorr[,2:3] -->

<!-- # Calculate the correlation coeficient  -->
<!-- correlation_coeff <- cor(x = forCorr$pre, y = forCorr$post, use = "pairwise.complete.obs", method = "pearson") -->
<!-- ``` -->

<!-- ```{r Final N} -->
<!-- # Number of complete cases -->
<!-- length(!is.na(forCorr[,1] & forCorr[,2])) -->
<!-- ``` -->

<!-- ## Plots of outliers -->
<!-- ### Plots of cleaned, averaged ssrts -->
<!-- ```{r Look at ssrt_avg outliers in cleaned data} -->
<!-- p <- ggplot(data = df_ssrt, aes(x = prepost, ssrt_avg))  -->

<!-- # Boxplot -->
<!-- p + -->
<!--     geom_boxplot(outlier.size = 4, outlier.colour = "green") + -->
<!--     geom_text(label = df_ssrt$id)  -->


<!-- # Line plot -->
<!-- p + -->
<!--     geom_line(aes(group = id, color = factor(condition))) -->
<!-- p + -->
<!--     geom_line(aes(group = id, color = factor(id))) -->

<!-- # Both plots overlaid -->

<!-- p + -->
<!--     geom_boxplot(outlier.size = 4, outlier.colour = "green") + -->
<!--     geom_text(label = df_ssrt$id) + -->
<!--     geom_line(aes(group = id, color = factor(id))) + -->
<!--     ggtitle("Averaged and Cleaned ssrts During Scans, Outliers in Green are Beyond 1.5 IQR") -->

<!-- rm(p) -->
<!-- ``` -->

<!-- ### Plots of raw ssrts from base and end scans -->
<!-- ```{r} -->
<!-- ggplot(subset(df_ssrt_rawscores, session_number %in% c("run1", "run2", "run13", "run14"))) + -->
<!--     aes(x = session_number, y = ssrt, label = id) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_boxplot(range = 2.5, outlier.size = 4, outlier.colour = "green") + -->
<!--     geom_text_layer + -->
<!--     ggtitle("Raw ssrts During Scans, Outliers in Green are Beyond 1.5 IQR") -->
<!-- ```  -->