---
title: 'REV Behavioral Data Analysis: SST'
author: "Krista DeStasio/Brendan Cullen"
date: "4/26/2017"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
## R version 3.4.3 ##
rm(list = ls())
setwd("~/Desktop/REV_scripts/behavioral/REV_SST/scripts/analyses/")

## Install and load required packages
list.of.packages <- c("stringr", "tidyverse", "reshape2", "ggplot2", "psych", "gridExtra", "knitr", "lme4", "memisc", "withr", "ez")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])] 
if (length(new.packages)) install.packages(new.packages, repos = "http://cran.us.r-project.org")
lapply(list.of.packages, library, character.only = TRUE)

knitr::opts_chunk$set(fig.width = 12, fig.height = 8, fig.path = 'Figs/', echo = TRUE, warning = FALSE, message = FALSE)
```

### Key:

**Key to Stop-signal task components:**  

**SSD** -- Stop-signal delay -- _Time from go stimulus to stop signal_  
**RT** -- Reaction time -- _Time from go stimulus to button press_  
**SSRT** -- Stop-signal response time -- _SSRT = (nth RT - mean SSD)_    
**Signal-inhibit trial** -- response witheld on a stop-signal trial -- _RT > (SSRT + SSD)_  
**Signal-respond trial** -- erroneous response on a stop-signal trial -- _RT < (SSRT + SSD)_  

### Note:  
Results calculated based on the inegration method of estimating the stop-signal response time (SSRT). This method helps to account for skewness of the RT distribution and anticipatory slowing in advance of the stop stignal. As recommended in:  

>Verbruggen, F., Chambers, C. D., & Logan, G. D. (2013). Fictitious inhibitory differences: how skewness and slowing distort the estimation of stopping latencies. _Psychological Science, 24(3)_, 352–62. https://doi.org/10.1177/0956797612457390  

The integration method finds "the point at which the integral equals equals the probability of responding, $p(respond|signal)$, for a specific delay." 

```{r Create the participant ID and condition variables}
ID <- as.factor(c(1:144)) # Create the subject ID column
condition <- c(0, 1, 0, 0, 0, 1, 1, 0, 1, 0, 0, 1, 1, 1, 1, 1, 0, 0, 1, 0, 1, 1, 1, 0, 1, 1, 0, 0, 0, 1, 1, 1, 1, 0, 1, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 1, 0, 1, 0, 1, 1, 0, 0, 0, 1, 1, 1, 0, 1, 0, 1, 1, 1, 0, 0, 0, 0, 0, 1, 0, 0, 1, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 1, 1, 0, 1, 1, 0, 1, 0, 1, 1, 1, 1, 0, 0, 1, 1, 1, 1, 1, 0, 0, 1, 1, 1, 1, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 1, 0, 1, 1, 0, 0, 1, 0, 1, 1, 0, 1, 1, 1, 0, 0, 1, 0) # Match the participant to their condition
condition <- factor(condition, labels = c("control", "train"))
```

```{r Import task data}
## Import the SSRT results output from the extractAllSSTResults.m script
SSRTdata <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/singleVarTxts/REV_SSRTint16.txt",
  sep = "\t", header = FALSE)
## No Response Counts
noResponseCount <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/initialCheck/NRCount.txt",
  sep = "\t", header = FALSE)
## Wrong Go Counts
wrongGoCount <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/initialCheck/wrongGoCount.txt",
  sep = "\t", header = FALSE)
## Percent inhibition
pctInhibition <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/singleVarTxts/REV_PctInhib16.txt",
  sep = "\t", header = FALSE)
```

```{r Put all data frames in long form}
# Make a vector containing all the dataframes
dfs <- c("noResponseCount", "wrongGoCount", "pctInhibition", "SSRTdata") 

# Name the columns for each data frame by the run number
for (df in dfs) {
  df_tmp <- get(df)
  names(df_tmp) <- c("run1", "run2","run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12", "run13", "run14")
  assign(df, df_tmp)
}

# Append the participant IDs and conditions to the front of each data frame
for (df in dfs) {
    df_tmp <- get(df)
    df_tmp <- cbind(ID, condition, df_tmp)
    assign(df, df_tmp)
}

# Put the data frames in long form and append "_long" to the data frame name
for (df in dfs) {
    df_tmp <- get(df)
    df_tmp <- melt(data = df_tmp, idvars = ID, measure.vars = c("run1", "run2","run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12", "run13", "run14"), variable.name = "time", value.name = df)
    assign(paste(df, "_long", sep = ""),df_tmp)
}
```

```{r Create a single data frame}
df_rawSSRT <- cbind(SSRTdata_long, noResponseCount_long[,4], wrongGoCount_long[,4], pctInhibition_long[,4])
colnames(df_rawSSRT) <- c("ID", "condition", "time", "SSRT", "numNoResponse", "numWrongGo", "pctInhibition")

# Replace NaNs with Na
df_rawSSRT[ is.na(df_rawSSRT) ] <- NA
```

# Visualizing Participant Responses
Looking for: slow reaction times, lots of no responses, and weird (negative, super small, super big) SSRTs

## Cut-offs
Cut-off values are determined by visual inspection of the scatterplots, which are presented below in raw and trimmed form.  

- Non-Responses  
    + During Training: upper limit 25  
    + During Scans: upper limit 50  
- Wrong Go Count   
    + During Training (training group only): upper limit 25  
    + During Scans: upper limit 25   
- Percent inhibition
    + During Scans: lower limit 15, upper limit 75
    + During Training (training group only): lower limit 15, upper limit 75
- SSRTs
    + During Training: upper limit 500
    + During Scanning: upper limit 850, lower limit 100
    
```{r make new data frame}
df_SSRT <- df_rawSSRT
```

```{r runs omitted pct inhibition}
### PERCENT INHIBITION ###
## Replace SSRTs with NAs if percent inihibition is > 75 | < 20 during scans (all participants)

df_SSRT <- df_SSRT %>% 
    mutate(SSRT = replace(SSRT, 
                         which(pctInhibition > 75 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14" | pctInhibition < 20 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14"), NA)) # Baseline Scans

## Replace the percent inhibition with NAs if they  > 75 | < 20 during scans (all participants)

# df_SSRT <- df_SSRT %>%
#     mutate(pctInhibition = replace(pctInhibition,
#                                   which(pctInhibition < 20  & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14" | pctInhibition > 75 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14"), NA)) # Baseline Scans

# Look at which participants had runs removed & how many
outliers1 <- (!df_rawSSRT$SSRT %in% df_SSRT$SSRT)

outliers_pctInhib <- as.data.frame(table(df_rawSSRT[outliers1,]$ID))
colnames(outliers_pctInhib) <- c("ID", "outliers_pctInhib")
```

```{r Remove problem runs no-response}
### NO RESPONSE ###
## Replace the SSRTs with NAs if no-responses are > 50 during scans
df_SSRT <- df_SSRT %>% 
    mutate(SSRT = replace(SSRT, 
                         which(numNoResponse > 50 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14"), NA)) # Baseline Scans

# df_SSRT <- df_SSRT %>% 
#     mutate(numNoResponse = replace(numNoResponse, 
#                                   which(numNoResponse > 50 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14" | pctInhibition < 20 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14"), NA)) # Baseline Scans

# Look at which participants had runs removed & how many
outliers2 <- (!df_rawSSRT$SSRT %in% df_SSRT$SSRT)
outliers_noResponse <- as.data.frame(table(df_rawSSRT[outliers2,]$ID))
colnames(outliers_noResponse) <- c("ID", "Runs_omitted_noResponse")
```

```{r Remove problem runs wrong no-gos}
### WRONG GO ###
## Replace the SSRTs with NAs if wrong-gos are > 25 during scans (all participants)

df_SSRT <- df_SSRT %>% 
    mutate(SSRT = replace(SSRT, 
                           which(numWrongGo > 25 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14"), NA)) # Scans

## Replace the wrong-gos with NAs if they are > 25 during scans (all participants)

# df_SSRT <- df_SSRT %>% 
#     mutate(numWrongGo = replace(numWrongGo, 
#                         which(numWrongGo > 25 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14"), NA)) # Baseline Scan

# Look at which participants had runs removed & how many
outliers3 <- (!df_rawSSRT$SSRT %in% df_SSRT$SSRT)
outliers_wrongGo <- as.data.frame(table(df_rawSSRT[outliers3,]$ID))
colnames(outliers_wrongGo) <- c("ID", "Runs_omitted_wrongGo")
```

```{r runs omitted SSRT}
### SSRT ###
## Replace the SSRTs with NAs if they are > 850 | < 100 during scans (all participants)

df_SSRT <- df_SSRT %>% 
    mutate(SSRT = replace(SSRT,
                         which(SSRT > 850 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14" | SSRT < 100 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" & time != "run13" & time != "run14"), NA)) # Baseline Scans

# Look at which participants had runs removed & how many
outliers4 <- (!df_rawSSRT$SSRT %in% df_SSRT$SSRT)
outliers_ssrt <- as.data.frame(table(df_rawSSRT[outliers4,]$ID))
colnames(outliers_ssrt) <- c("ID", "Runs_omitted_ssrt")
```

```{r}
df_omitted_runs <- cbind(df_SSRT, outliers1, outliers2, outliers3, outliers4)
df_omitted_runs <- filter(df_omitted_runs, (outliers1 == TRUE | outliers2 == TRUE | outliers3 == TRUE | outliers4 == TRUE))
(df_omitted_runs <- sort(df_omitted_runs[,c(1,3)]))
length(unique(as.numeric(df_omitted_runs$ID)))
```

## View omitted runs
```{r Create a table of omitted runs}
# See omitted
dfs <- list(outliers_pctInhib, outliers_noResponse, outliers_wrongGo, outliers_ssrt)
outliers_tableFull <- plyr::join_all(dfs, by = "ID")
outliers_table <- outliers_tableFull[which(outliers_tableFull$Runs_omitted_ssrt != 0),]
kable(outliers_table, caption = "Runs Omitted (columns are cumulative)")
summary(outliers_tableFull$Runs_omitted_ssrt)
```

## Notes on problem runs

- 134 - kept switching correct/incorrect direction presses.  
- 82 - switched buttons 1/2 way through run 7.  
- 91 - stopped trying for last part of run 3. Repeatedly pressing same key (not an assigned key).  
- 26 - Participant in experimental condition, but has 0% inhibition during all training runs.  
- 51 - Why doesn't 51 have the base scan SSRTs?   
    + Can't be calculated due to high number of non-responses and wrong-gos.  
- 138 - Why doesn't 138 have the base scan SSRTs?   
    + Can't be calculated due to high number of wrong-gos.  
    
    
    
```{r Subset only the scan data and convert long to wide}
# select only scan data (get rid of training data)
df_SSRT <- subset(df_SSRT,time %in% c("run1", "run2"))[,c("ID","time","SSRT")] %>%
  spread(time, SSRT)

# re-name SSRT vars to be more specific
names(df_SSRT)[names(df_SSRT)=="run1"] <- "SSRT_run1"
names(df_SSRT)[names(df_SSRT)=="run2"] <- "SSRT_run2"

# Create vars that represent mean SSRT across available runs for baseline and endpoint scans
df_SSRT$SSRT_base_mean <- rowMeans(df_SSRT[,c("SSRT_run1","SSRT_run2")], na.rm = TRUE)
```

## Write list of omitted runs to an excel file
```{r}
write.csv(df_omitted_runs, file = "~/Desktop/df_omitted_runs.csv", row.names = FALSE)
```

## NOT USING THIS PART OF THE ORIGINAL CODE

<!-- ## Comparison Plots: Raw vs. Cleaned Data   -->
<!-- ```{r Create plots of the data} -->
<!-- ### CHECKING FOR PROBLEMS ### -->
<!-- ## Plot All Non-responses -->
<!-- noResp_raw <- ggplot(df_rawSSRT, aes(x = time, y = numNoResponse, label = ID)) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_text(aes(label = ifelse(numNoResponse > 10,as.character(ID),'')),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!--     ggtitle("Num of Non-Responses Raw Data, \nAll Participants, All Time Points") -->

<!-- ## Plot Wrong Go Count, Scans, All Participants -->
<!-- wrongGo_rawAll <- ggplot(subset(df_rawSSRT, time %in% c("run1", "run2", "run13", "run14"))) + -->
<!--     aes(x = time, y = numWrongGo, label = ID) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!--     ggtitle("Wrong Go Count During Scans \nRaw Data, All Participants") -->

<!-- # ## Plot Wrong Gos During Training, Training Group Only -->
<!-- # wrongGo_rawTrn <- ggplot(subset(df_rawSSRT,time %in%  c("run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12") & condition == "train")) + -->
<!-- #     aes(x = time, y = numWrongGo, label = ID) + -->
<!-- #     geom_point(na.rm = TRUE) + -->
<!-- #     geom_text(aes(label = ifelse(numWrongGo > 25,as.character(ID),'')),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!-- #     ggtitle("Wrong Go Count During Training \nRaw Data, Training Group Only") -->

<!-- ## Plot SSRTs during Scan -->
<!-- SSRT_rawScan <- ggplot(subset(df_rawSSRT,time %in% c("run1", "run2", "run13", "run14"))) + -->
<!--     aes(x = time, y = SSRT, label = ID) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!--     ggtitle("SSRTs During Scans, \nAll Participants") -->

<!-- # ## Plot SSRTs during training, only for the training group -->
<!-- # SSRT_rawTrn <- ggplot(subset(df_rawSSRT, time %in%  c("run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12") & condition == "train")) + -->
<!-- #     aes(x = time, y = SSRT, label = ID) + -->
<!-- #     geom_point(na.rm = TRUE) + -->
<!-- #     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!-- #     ggtitle("SSRTs During Training Raw Data, \nTraining Group Only") -->

<!-- ## Plot Pct inhibition during Scan -->
<!-- PctInhib_rawScan <- ggplot(subset(df_rawSSRT,time %in% c("run1", "run2", "run13", "run14"))) + -->
<!--     aes(x = time, y = pctInhibition, label = ID) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!--     ggtitle("Percent Inhibition During Scans, \nAll Participants") -->

<!-- # ## Plot Percent Inhibition during training for the training group  -->
<!-- # pctInhib_rawTrn <- ggplot(subset(df_rawSSRT, time %in% c("run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12") & condition == "train")) + -->
<!-- #     aes(x = time, y = pctInhibition, label = ID) + -->
<!-- #     geom_point(na.rm = TRUE) + -->
<!-- #     geom_jitter(width = 0.25) + -->
<!-- #     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!-- #     ggtitle("Percent Inhibition Raw Data, \nTraining Group During Training") -->

<!-- ### CLEANED DATA ### -->

<!-- ## Plot All Non-responses -->
<!-- noResp_clean <- ggplot(df_SSRT, aes(x = time, y = numNoResponse, label = ID)) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_text(aes(label = ifelse(numNoResponse > 10,as.character(ID),'')),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!--     ggtitle("Non-Responses, All P's, All Times, \nUpper Limits: Training 25, Scans 50") -->

<!-- ## Plot Wrong Go Count, Scans, All Participants -->
<!-- wrongGo_cleanAll <- ggplot(subset(df_SSRT, time %in% c("run1", "run2", "run13", "run14"))) + -->
<!--     aes(x = time, y = numWrongGo, label = ID) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!--     ggtitle("Wrong Gos During Scans, All P's, \nUpper Limit Cut-Off of 25") -->

<!-- # ## Plot Wrong Gos During Training, Training Group Only -->
<!-- # wrongGo_cleanTrn <- ggplot(subset(df_SSRT,time %in%  c("run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12") & condition == "train")) + -->
<!-- #     aes(x = time, y = numWrongGo, label = ID) + -->
<!-- #     geom_point(na.rm = TRUE) + -->
<!-- #     geom_text(aes(label = ifelse(numWrongGo > 25,as.character(ID),'')),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!-- #     ggtitle("Wrong Go's During Training, \nTraining Group Only, Upper Limit 25") -->

<!-- # ## Plot Pct Inhibition during training, training group only  -->
<!-- # PctInhib_cleanTrn <- ggplot(subset(df_SSRT, time %in%  c("run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12") & condition == "train")) + -->
<!-- #     aes(x = time, y = pctInhibition, label = ID) + -->
<!-- #     geom_point(na.rm = TRUE) + -->
<!-- #     geom_text(aes(label = as.character(ID)), hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!-- #     ggtitle("Percent Inhibition During Training, \nTraining Group Only, Lower Limit 15, Upper Limit 75") -->

<!-- ## Plot pct inhib during scans for all participants -->
<!-- PctInhib_cleanScan <- ggplot(subset(df_SSRT,time %in% c("run1", "run2", "run13", "run14"))) + -->
<!--     aes(x = time, y = pctInhibition, label = ID) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!--     ggtitle("Pct Inhibition During Scans, All P's, \n Lower Limit 15, Upper Limit 75") -->

<!-- ## Plot SSRTs during Scan -->
<!-- SSRT_cleanScan <- ggplot(subset(df_SSRT,time %in% c("run1", "run2", "run13", "run14"))) + -->
<!--     aes(x = time, y = SSRT, label = ID) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!--     ggtitle("SSRTs During Scans, All P's, \nUpper Limit 850, Lower Limit 100") -->

<!-- # ## Plot SSRTs during training, only for the training group -->
<!-- # SSRT_cleanTrn <- ggplot(subset(df_SSRT, time %in%  c("run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12") & condition == "train")) + -->
<!-- #     aes(x = time, y = SSRT, label = ID) + -->
<!-- #     geom_point(na.rm = TRUE) + -->
<!-- #     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!-- #     ggtitle("SSRTs During Training, \nTraining Group, Upper Limit 500") -->
<!-- ``` -->

<!-- ### Wrong Gos   -->

<!-- ```{r Plot wrong-gos} -->
<!-- # Define grid layout to locate plots and print each graph -->
<!-- grid.arrange(wrongGo_rawAll, wrongGo_cleanAll, ncol = 2) -->
<!-- grid.arrange(wrongGo_rawTrn, wrongGo_cleanTrn, ncol = 2) -->
<!-- ``` -->

<!-- ### Non-Responses -->
<!-- ```{r Plot non-responses} -->
<!-- grid.arrange(noResp_raw, noResp_clean, ncol = 2) -->
<!-- ``` -->

<!-- ### Percent Inhibition -->
<!-- ```{r Plot percent inhibition} -->
<!-- grid.arrange(PctInhib_rawScan,PctInhib_cleanScan, ncol = 2) -->
<!-- grid.arrange(pctInhib_rawTrn, PctInhib_cleanTrn, ncol = 2) -->
<!-- ``` -->

<!-- ### SSRTs -->
<!-- ```{r plot SSRTs} -->
<!-- grid.arrange(SSRT_rawScan, SSRT_cleanScan, ncol = 2) -->
<!-- grid.arrange(SSRT_rawTrn, SSRT_cleanTrn, ncol = 2) -->
<!-- ``` -->

<!-- ## Description of Omitted Runs by Participant -->
<!-- ```{r Compare clean and raw data} -->
<!-- ## Compare raw and cleaned data frames to find how many runs dropped by participant. Get avg. dropped, min, max, and outliers. -->
<!-- omitted_runs <- (!df_rawSSRT$SSRT %in% df_SSRT$SSRT) -->

<!-- # Plot the number of omitted runs by participant ID -->
<!-- ggplot(df_rawSSRT[omitted_runs,], aes(x = ID)) + -->
<!--     geom_bar() + -->
<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
<!--     ggtitle("Number of Runs Omitted Per Participant") + -->
<!--     labs(x = "Participant ID", y = "Number of Runs Omitted") -->

<!-- runOmit <- as.data.frame(table(df_rawSSRT[omitted_runs,]$ID)) -->
<!-- summary(runOmit$Freq) -->
<!-- ``` -->

<!-- ```{r Create the Pre and Post average SSRT scores, include=FALSE} -->
<!-- # Make a column in the dataframe called prepost. If the run numbers are 1 or 2, put "pre" in the new column. If run num = 13 or 14, put "post" in the new column -->
<!-- df_SSRT$prepost <- ifelse(df_SSRT$time %in% c("run1", "run2"), "pre", ifelse(df_SSRT$time %in% c("run13", "run14"), "post", NA)) -->

<!-- # Take the mean of cells for which IDs match and prepost matches -->
<!-- df_avgSSRT <- df_SSRT %>% group_by(ID, prepost) %>% summarise(mean(SSRT, na.rm = TRUE))  -->

<!-- # Keep only average values for pre and post, discard avg. training SSRT -->
<!-- df_avgSSRT <- df_avgSSRT[ which(df_avgSSRT$prepost == "pre" | df_avgSSRT$prepost == "post"), ]  -->
<!-- df_avgSSRT$prepost <- as.factor(df_avgSSRT$prepost) # Make prepost a factor -->
<!-- df_avgSSRT <- df_avgSSRT[order(df_avgSSRT$prepost),] # Order values in the data frame by the prepost column -->

<!-- condition_twice <- rep(condition, 2) -->
<!-- condition <- cbind(condition_twice) -->
<!-- condition <- factor(condition, labels = c("control", "train")) -->

<!-- df_avgSSRT <- merge(condition, df_avgSSRT, by = 0) -->
<!-- df_avgSSRT <- df_avgSSRT[order(df_avgSSRT$ID),] -->
<!-- df_avgSSRT <- df_avgSSRT[,2:5] -->
<!-- colnames(df_avgSSRT) <- c("condition", "ID", "time", "SSRT_avg") -->
<!-- ``` -->

<!-- ## Final Sample Viable Training Sessions -->
<!-- ```{r Plot how many viable runs participants have} -->
<!-- # Count the viable sessions during "training" for the training group -->
<!-- df_viable_train <- subset(df_SSRT, condition == "train") -->
<!-- df_viable_train <- df_viable_train[ which(df_viable_train$time != "run1" & df_viable_train$time != "run2" & df_viable_train$time != "run13"  & df_viable_train$time != "run14"), ] -->
<!-- df_viable_train <- df_viable_train %>% group_by(ID) %>% summarize(ViableN = sum(!is.na(SSRT))) -->

<!-- # Plot the training group -->
<!-- viable_trn <- qplot(df_viable_train$ViableN, geom = "bar", xlab = "Viable SST Runs", ylab = "Count", main = "Viable Training Sessions, Training Group") -->

<!-- # Count the viable sessions during "training" for the conrol group -->
<!-- df_viable_control <- subset(df_SSRT, condition == "control") -->
<!-- df_viable_control <- df_viable_control[ which(df_viable_control$time != "run1" & df_viable_control$time != "run2" & df_viable_control$time != "run13" & df_viable_control$time != "run14"), ] -->
<!-- df_viable_control <- df_viable_control %>% group_by(ID) %>% summarize(ViableN = sum(!is.na(SSRT))) -->

<!-- # Plot the control group -->
<!-- viable_contr <- qplot(df_viable_control$ViableN, geom = "bar", xlab = "Viable SST Runs", ylab = "Count", main = "Viable Training Sessions, Control Group") -->

<!-- grid.arrange(viable_trn, viable_contr, ncol = 2) -->
<!-- ``` -->

<!-- **Count of viable training sessions (out of 10 possible), training group:** -->
<!-- ```{r plot viable sessions for training group} -->
<!-- table(df_viable_train$ViableN) -->
<!-- ``` -->

<!-- **Count of viable training sessions (out of 10 possible), control group:** -->
<!-- ```{r plot viable sessions for control group} -->
<!-- table(df_viable_control$ViableN) -->
<!-- ``` -->

<!-- **Who was excluded based on too few training sessions?** -->
<!-- ```{r Excluded based on viable training sessions} -->
<!-- ## Exclude participants with too few training sessions -->
<!-- (exclude <- as.numeric(df_viable_train$ID[(df_viable_train$ViableN < 6)])) -->
<!-- ``` -->

<!-- ```{r Create data frames for analysis} -->
<!-- ## Data frame containing pre/post averages, participants excluded based on too few training sessions -->
<!-- df_SSRTprepost <- df_avgSSRT %>% mutate(SSRT_avg = replace(SSRT_avg, which(ID %in% exclude), NA)) -->
<!-- df_SSRTprepost[ is.na(df_SSRTprepost) ] <- NA -->

<!-- ## Data frame with all runs, participants excluded based on above criteria -->
<!-- df_SSRTclean <- df_SSRT %>% mutate(SSRT = replace(SSRT, which(ID %in% exclude), NA)) -->

<!-- ## Data frame with all runs and average base and end SSRT, participants not excluded based on too few runs -->
<!-- colnames(df_avgSSRT) <- c("condition", "ID", "prepost", "SSRT_avg") -->
<!-- df_SSRTallSubs <- merge(df_SSRT,df_avgSSRT, by = c("ID", "condition", "prepost"), all.x = TRUE) -->

<!-- # Label prepost only for runs 1 and 14 -->
<!-- df_SSRTallSubs <- df_SSRTallSubs %>%  -->
<!--     mutate(prepost = replace(prepost,  -->
<!--                                   which(time != "run1" & time != "run14"), NA)) -->
<!-- df_SSRTallSubs <- df_SSRTallSubs %>%  -->
<!--     mutate(SSRT_avg = replace(SSRT_avg,  -->
<!--                                   which(time != "run1" & time != "run14"), NA)) -->

<!-- df_SSRTallSubs$prepost <- as.factor(df_SSRTallSubs$prepost) -->
<!-- str(df_SSRTallSubs) -->
<!-- # Export full data frame -->
<!-- save(df_SSRTallSubs, file = "df_SSRT.Rda") -->
<!-- ``` -->

<!-- # Analyses of SSRT Data -->
<!-- ## Pre-post change in SSRT -->

<!-- ### Multilevel model test of primary hypothesis -->
<!-- ```{r Model pre-post change with lmer} -->
<!-- df_SSRTprepost$time <- relevel(df_SSRTprepost$time, ref = "pre") # make baseline the reference group -->

<!-- # Keep only participants with base and end session data -->
<!-- SSRTcomplete <- df_SSRTprepost[complete.cases(df_SSRTprepost),] -->
<!-- tt <- table(SSRTcomplete$ID) -->
<!-- SSRTcomplete <- SSRTcomplete[SSRTcomplete$ID %in% names(tt[tt > 1]), ] -->
<!-- SSRTcomplete$ID <- factor(SSRTcomplete$ID) -->
<!-- SSRTcomplete$time <- factor(SSRTcomplete$time) -->
<!-- SSRTcomplete$condition <- factor(SSRTcomplete$condition) -->

<!-- # Multilevel model with intercept allowed to vary & fixed slopes for time & condition -->
<!-- multilevel_model <- lmer( SSRT_avg ~ time*condition + (1 |ID), data = SSRTcomplete ) -->
<!-- kable(round(anova(multilevel_model),2)) # have to use anova table rather than summary -->
<!-- #model_norand <- lm( SSRT_avg ~ time*condition, data = SSRTcomplete ) -->
<!-- ``` -->

<!-- ### Repeated measures ANOVA test of main hypothesis for comparison -->
<!-- ```{r Model pre-post change with ezANOVA and lmer} -->
<!-- # Repeated measures ANOVA with SSRT as DV, time as within subs factor, and condition as between subs factor -->
<!-- ezmultilevel_model <- ez::ezANOVA(data = SSRTcomplete, dv = SSRT_avg, wid = ID, within = time, between = condition, type = 3, detailed = TRUE)  -->
<!-- kable(ezmultilevel_model$ANOVA) -->
<!-- ``` -->

<!-- ### Plots -->
<!-- ```{r Bar plot of pre-post change in SSRT} -->
<!-- # calculate the means to plot -->
<!-- #SSRTcomplete$condition <- as.numeric(SSRTcomplete$condition) -->
<!-- #SSRTcomplete$prepost <- as.numeric(SSRTcomplete$prepost) -->
<!-- groups <- group_by(SSRTcomplete, condition, time) -->
<!-- plot_data <- dplyr::summarise(groups,  -->
<!--                        mean = mean(SSRT_avg, na.rm = TRUE), -->
<!--                        sd = sd(SSRT_avg, na.rm = TRUE), -->
<!--                        n = n()) -->
<!-- plot_data <- mutate(plot_data, -->
<!--                     se = sd/sqrt(n), -->
<!--                     ci = qt(0.975,df = n-1)*se) -->

<!-- # Re-level and rename the condition factor for plotting -->
<!-- plot_data$condition <- factor(plot_data$condition, levels(plot_data$condition)[c(2,1)]) -->
<!-- plot_data$condition <- plyr::revalue(plot_data$condition, c("train" = "Training", "control" = "Control")) -->

<!-- # Bar graph of pre-post change by condition with standard error bars. -->

<!-- ggplot(plot_data, aes(x = condition, y = mean, fill = interaction(time, condition))) + -->
<!--    geom_bar(stat = "identity", position = position_dodge(), color = "black", size = .3) + -->
<!--   geom_errorbar(aes(ymin = mean - ci, ymax = mean + ci),  -->
<!--                 size = .8, -->
<!--                 width = .2, -->
<!--                 position = position_dodge(.9)) + -->
<!--     xlab("Condition") + -->
<!--     ylab("SSRT (ms)") + -->
<!-- scale_fill_manual(values = c("#28B463", "#90EE90", "#4169E1", "#87CEEB"),name = "Time",  -->
<!--               labels = c("Baseline", "Endpoint", "Baseline","Endpoint")) + -->
<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
<!--     ggtitle("Mean Stop-Signal Reaction Time at \nPre and Post Intervention by Condition") + -->
<!--     coord_cartesian(ylim = c(200, 320))  + -->
<!--     scale_y_continuous(breaks = seq(200, 320, 10)) + -->
<!--     theme(axis.text = element_text(size = 24), -->
<!--         axis.title = element_text(size = 24, face = "bold"), -->
<!--         legend.title = element_text(size = 14, face = "bold"), -->
<!--         legend.position = c(.98, .98), -->
<!--         legend.justification = c("right", "top"), -->
<!--         legend.key.size = unit(.5, "cm"), -->
<!--         legend.text = element_text(size = 14), -->
<!--         title = element_text(size = 24)) -->
<!-- ``` -->

<!-- ```{r plot the model data} -->
<!-- ggplot(SSRTcomplete, aes(x = time, y = SSRT_avg, fill = condition)) + -->
<!--     geom_boxplot(na.rm = TRUE) + -->
<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
<!--     ggtitle("Pre and Post Stop Signal \nResponse Time (SSRT) by Group") +  -->
<!--     labs(x = "Time Point", y = "Stop Signal Response Time") + -->
<!--     scale_fill_discrete(name = "Condition", -->
<!--                          breaks = c("control", "train"), -->
<!--                          labels = c("Control", "Training")) -->
<!-- ``` -->

<!-- ## Final sample  -->
<!-- ```{r final sample description} -->
<!-- (table(SSRTcomplete$condition))/2 -->
<!-- included_IDs <- dimnames(table(SSRTcomplete$ID)) -->
<!-- save(included_IDs, file = "Included_IDs.rda") -->
<!-- ``` -->

<!-- # Training sessions -->
<!-- ## Linear effect of time within the training sessions (in the training group) -->
<!-- ```{r Use lmer to examine training slopes} -->
<!-- ## Create data frame of only training sessions for training group only -->
<!-- df_SSRTtrain <- subset(df_SSRTclean, condition == "train" & time != "run1" & time != "run2" & time != "run13" & time != "run14")  -->
<!-- ## Data frame of only training sessions, both control and training groups -->
<!-- df_SSRT10ses <- subset(df_SSRTclean, time != "run1" & time != "run2" & time != "run13" & time != "run14")  -->

<!-- # Model -->
<!-- df_SSRTtrain$time <- as.numeric(df_SSRTtrain$time) -->
<!-- mlmodel <- lmer( SSRT ~ time + (1 + time|ID), data = df_SSRTtrain ) -->
<!-- summary(mlmodel) -->

<!-- df_SSRT10ses$time <- as.numeric(df_SSRT10ses$time) -->
<!-- full_mlModel <- lmer( SSRT ~ condition*time + (1 + time | ID), data = df_SSRT10ses) -->
<!-- summary(full_mlModel) -->
<!-- ``` -->

<!-- ## Plots -->
<!-- ```{r Boxplots of SST performance across time} -->
<!-- ggplot(subset(df_SSRTclean, condition == "train" | condition == "control" & time %in% c("run1", "run2", "run13", "run14"))) +  -->
<!--     aes(x = time, y = SSRT, fill = condition) + -->
<!--     geom_boxplot(na.rm = TRUE) + -->
<!--     coord_flip() + -->
<!--     scale_x_discrete(limits = rev(levels(df_SSRTclean$time))) + -->
<!--     theme(plot.title = element_text(hjust = 0.5)) + -->
<!--     ggtitle("Stop Signal Response Times \nby Time and Group") + -->
<!--     labs(x = "Time Point", y = "Stop Signal Response Time") + -->
<!--     scale_fill_discrete(name = "Condition", -->
<!--                          breaks = c("control", "train"), -->
<!--                          labels = c("Control", "Training")) -->
<!-- ``` -->

<!-- # Post-hoc -->
<!-- ## Partial eta-squared -->
<!-- ```{r Partial eta-squared} -->
<!-- anova_table <- anova(multilevel_model) -->
<!-- SS_interaction <- anova_table$'Sum Sq'[3] -->

<!-- mlm_summary <- summary(multilevel_model) -->
<!-- SS_error <- sum(mlm_summary$residuals^2) -->
<!-- partial_etasq <- SS_interaction / (SS_interaction + 3705.7) -->
<!-- meanSqError <- 3705.7 -->

<!-- ``` -->

<!-- ## Correlation coefficient for pre & post SSRT -->
<!-- ```{r Correlation coefficient} -->
<!-- # Create a date frame with averaged SSRT scores in separate columns for pre and post sessions -->
<!-- forCorr <- dcast(data = SSRTcomplete, formula = ID ~ time, fun.aggregate = sum, value.var = "SSRT_avg") -->
<!-- forCorr <- forCorr[,2:3] -->

<!-- # Calculate the correlation coeficient  -->
<!-- correlation_coeff <- cor(x = forCorr$pre, y = forCorr$post, use = "pairwise.complete.obs", method = "pearson") -->
<!-- ``` -->

<!-- ```{r Final N} -->
<!-- # Number of complete cases -->
<!-- length(!is.na(forCorr[,1] & forCorr[,2])) -->
<!-- ``` -->

<!-- ## Plots of outliers -->
<!-- ### Plots of cleaned, averaged SSRTs -->
<!-- ```{r Look at SSRT_avg outliers in cleaned data} -->
<!-- p <- ggplot(data = df_SSRTprepost, aes(x = time, SSRT_avg))  -->

<!-- # Boxplot -->
<!-- p + -->
<!--     geom_boxplot(outlier.size = 4, outlier.colour = "green") + -->
<!--     geom_text(label = df_SSRTprepost$ID)  -->


<!-- # Line plot -->
<!-- p + -->
<!--     geom_line(aes(group = ID, color = factor(condition))) -->
<!-- p + -->
<!--     geom_line(aes(group = ID, color = factor(ID))) -->

<!-- # Both plots overlaid -->

<!-- p + -->
<!--     geom_boxplot(outlier.size=4, outlier.colour = "green") + -->
<!--     geom_text(label = df_SSRTprepost$ID) + -->
<!--     geom_line(aes(group = ID, color = factor(ID))) + -->
<!--     ggtitle("Averaged and Cleaned SSRTs During Scans, Outliers in Green are Beyond 1.5 IQR") -->
<!-- ``` -->

<!-- ### Plots of raw SSRTs from base and end scans -->
<!-- ```{r} -->
<!-- ggplot(subset(df_rawSSRT, time %in% c("run1", "run2", "run13", "run14"))) + -->
<!--     aes(x = time, y = SSRT, label = ID) + -->
<!--     geom_point(na.rm = TRUE) + -->
<!--     geom_boxplot(range = 2.5, outlier.size = 4, outlier.colour = "green") + -->
<!--     geom_text(aes(label = as.character(ID)),hjust = 0, vjust = 0, na.rm = TRUE) + -->
<!--     ggtitle("Raw SSRTs During Scans, Outliers in Green are Beyond 1.5 IQR") -->
<!-- ```  -->