---
title: 'List of runs and IDs to exclude from analyses'
author: "Krista DeStasio/Brendan Cullen"
date: "4/26/2017"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
## R version 3.4.3 ##
rm(list = ls())
setwd("~/Desktop/REV_scripts/behavioral/REV_SST/scripts/analyses/")
outputDir = '~/Desktop/REV_scripts/behavioral/REV_SST/output'

## Install and load required packages
list.of.packages <- c("stringr", "tidyverse", "reshape2", "ggplot2", "psych", "gridExtra", "knitr", "lme4", "memisc", "withr", "ez", "arsenal")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])] 
if (length(new.packages)) install.packages(new.packages, repos = "http://cran.us.r-project.org")
lapply(list.of.packages, library, character.only = TRUE)

knitr::opts_chunk$set(fig.width = 12, fig.height = 8, fig.path = 'Figs/', echo = TRUE, warning = FALSE, message = FALSE)
```
# Purpose
Returns a list of participant IDs to omit based on behavioral data exclusion criteria.  
Returns SSRTs for each participant that is retained.  


### Key:

**Key to Stop-signal task components:**  

**SSD** -- Stop-signal delay -- _Time from go stimulus to stop signal_  
**RT** -- Reaction time -- _Time from go stimulus to button press_  
**SSRT** -- Stop-signal response time -- _SSRT = (nth RT - mean SSD)_    
**Signal-inhibit trial** -- response witheld on a stop-signal trial -- _RT > (SSRT + SSD)_  
**Signal-respond trial** -- erroneous response on a stop-signal trial -- _RT < (SSRT + SSD)_  

### Note:  
Results calculated based on the inegration method of estimating the stop-signal response time (SSRT). This method helps to account for skewness of the RT distribution and anticipatory slowing in advance of the stop stignal. As recommended in:  

>Verbruggen, F., Chambers, C. D., & Logan, G. D. (2013). Fictitious inhibitory differences: how skewness and slowing distort the estimation of stopping latencies. _Psychological Science, 24(3)_, 352–62. https://doi.org/10.1177/0956797612457390  

The integration method finds "the point at which the integral equals equals the probability of responding, $p(respond|signal)$, for a specific delay." 

```{r Create the participant ID and condition variables, include=FALSE}
ID <- as.factor(c(1:144)) # Create the subject ID column
condition <- c(0, 1, 0, 0, 0, 1, 1, 0, 1, 0, 0, 1, 1, 1, 1, 1, 0, 0, 1, 0, 1, 1, 1, 0, 1, 1, 0, 0, 0, 1, 1, 1, 1, 0, 1, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 1, 0, 1, 0, 1, 1, 0, 0, 0, 1, 1, 1, 0, 1, 0, 1, 1, 1, 0, 0, 0, 0, 0, 1, 0, 0, 1, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 1, 1, 0, 1, 1, 0, 1, 0, 1, 1, 1, 1, 0, 0, 1, 1, 1, 1, 1, 0, 0, 1, 1, 1, 1, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 1, 0, 1, 1, 0, 0, 1, 0, 1, 1, 0, 1, 1, 1, 0, 0, 1, 0) # Match the participant to their condition
condition <- factor(condition, labels = c("control", "train"))
```

```{r Import task data, include=FALSE}
## Import the SSRT results output from the extractAllSSTResults.m script
SSRTdata <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/singleVarTxts/REV_SSRTint16.txt",
  sep = "\t", header = FALSE)
## No Response Counts
noResponseCount <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/initialCheck/NRCount.txt",
  sep = "\t", header = FALSE)
## Wrong Go Counts
wrongGoCount <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/initialCheck/wrongGoCount.txt",
  sep = "\t", header = FALSE)
## Percent inhibition
pctInhibition <- read.table(
  "~/Desktop/REV_scripts/behavioral/REV_SST/compiledResults/upToREV144/singleVarTxts/REV_PctInhib16.txt",
  sep = "\t", header = FALSE)
```

```{r Put all data frames in long form, include=FALSE}
# Make a vector containing all the dataframes
dfs <- c("noResponseCount", "wrongGoCount", "pctInhibition", "SSRTdata") 

# Name the columns for each data frame by the run number
for (df in dfs) {
  df_tmp <- get(df)
  names(df_tmp) <- c("run1", "run2","run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12", "run13", "run14")
  assign(df, df_tmp)
}

# Append the participant IDs and conditions to the front of each data frame
for (df in dfs) {
    df_tmp <- get(df)
    df_tmp <- cbind(ID, condition, df_tmp)
    assign(df, df_tmp)
}

# Put the data frames in long form and append "_long" to the data frame name
for (df in dfs) {
    df_tmp <- get(df)
    df_tmp <- melt(data = df_tmp, idvars = ID, measure.vars = c("run1", "run2","run3", "run4", "run5", "run6", "run7", "run8", "run9", "run10", "run11", "run12", "run13", "run14"), variable.name = "time", value.name = df)
    assign(paste(df, "_long", sep = ""),df_tmp)
}
```

```{r Create a single data frame, include=FALSE}
df_rawSSRT <- cbind(SSRTdata_long, noResponseCount_long[,4], wrongGoCount_long[,4], pctInhibition_long[,4])
colnames(df_rawSSRT) <- c("ID", "condition", "time", "SSRT", "numNoResponse", "numWrongGo", "pctInhibition")

# Replace NaNs with Na
df_rawSSRT[ is.na(df_rawSSRT) ] <- NA
```

# Visualizing Participant Responses
Looking for: slow reaction times, lots of no responses, and weird (negative, super small, super big) SSRTs  

## Cut-offs
Cut-off values are determined by visual inspection of the scatterplots, which are presented below in raw and trimmed form.  

- Non-Responses  
    + During Training: upper limit 25  
    + During Scans: upper limit 50  
- Wrong Go Count   
    + During Training (training group only): upper limit 25  
    + During Scans: upper limit 25   
- Percent inhibition
    + During Scans: lower limit 15, upper limit 75
    + During Training (training group only): lower limit 15, upper limit 75
- SSRTs
    + During Training: upper limit 500
    + During Scanning: upper limit 850, lower limit 100
    
```{r make new data frame, include=FALSE}
df_SSRT <- df_rawSSRT
```

```{r runs omitted pct inhibition, echo=FALSE}
### PERCENT INHIBITION ###
## Replace SSRTs with NAs if percent inihibition is > 75 | < 20 during scans (all participants)

df_SSRT <- df_SSRT %>% 
    mutate(SSRT = replace(SSRT, 
                         which(pctInhibition > 75 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12"  | pctInhibition < 20 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" ), NA)) # Scans

# Look at which participants had runs removed & how many
compare_SSRT_pctInhib <- summary(arsenal::compare(df_rawSSRT, df_SSRT))
diff_SSRT_rows_pctInhib <- compare_SSRT_pctInhib[["diffs.table"]][["row.x"]]
outliers_pctInhib_count <- as.data.frame(table(df_rawSSRT[diff_SSRT_rows_pctInhib,]$ID))
colnames(outliers_pctInhib_count) <- c("ID", "outliers_pctInhib_count")

# create new "outliers1" vector
outliers_pctInhib_logical <- row.names(df_SSRT) %in% diff_SSRT_rows_pctInhib
```

```{r Remove problem runs no-response, echo=FALSE}
### NO RESPONSE ###
## Replace the SSRTs with NAs if no-responses are > 50 during scans
df_SSRT <- df_SSRT %>% 
    mutate(SSRT = replace(SSRT, 
                         which(numNoResponse > 50 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" ), NA)) # Scans

# Look at which participants had runs removed & how many
compare_SSRT_noResponse <- summary(arsenal::compare(df_rawSSRT, df_SSRT))
diff_SSRT_rows_noResponse <- compare_SSRT_noResponse[["diffs.table"]][["row.x"]]
outliers_noResponse_count <- as.data.frame(table(df_rawSSRT[diff_SSRT_rows_noResponse,]$ID))
colnames(outliers_noResponse_count) <- c("ID", "outliers_noResponse_count")

# create new "outliers2" vector (cumulative)
outliers_noResponse_logical <- row.names(df_SSRT) %in% diff_SSRT_rows_noResponse
```

```{r Remove problem runs wrong no-gos, echo=FALSE}
### WRONG GO ###
## Replace the SSRTs with NAs if wrong-gos are > 25 during scans (all participants)

df_SSRT <- df_SSRT %>% 
    mutate(SSRT = replace(SSRT, 
                           which(numWrongGo > 25 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" ), NA)) # Scans

# Look at which participants had runs removed & how many
compare_SSRT_wrongGo <- summary(arsenal::compare(df_rawSSRT, df_SSRT))
diff_SSRT_rows_wrongGo <- compare_SSRT_wrongGo[["diffs.table"]][["row.x"]]
outliers_wrongGo_count <- as.data.frame(table(df_rawSSRT[diff_SSRT_rows_wrongGo,]$ID))
colnames(outliers_wrongGo_count) <- c("ID", "outliers_wrongGo_count")

# create new "outliers3" vector
outliers_wrongGo_logical <- row.names(df_SSRT) %in% diff_SSRT_rows_wrongGo
```

```{r runs omitted SSRT, echo=FALSE}
### SSRT ###
## Replace the SSRTs with NAs if they are > 850 | < 100 during scans (all participants)

df_SSRT <- df_SSRT %>% 
    mutate(SSRT = replace(SSRT,
                         which(SSRT > 850 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12"  | SSRT < 100 & time != "run3" & time != "run4" & time != "run5" & time != "run6" & time != "run7" & time != "run8" & time != "run9" & time != "run10" & time != "run11" & time != "run12" ), NA)) # Scans

# Look at which participants had runs removed & how many
compare_SSRT_ssrt <- summary(arsenal::compare(df_rawSSRT, df_SSRT))
diff_SSRT_rows_ssrt <- compare_SSRT_ssrt[["diffs.table"]][["row.x"]]
outliers_ssrt_count <- as.data.frame(table(df_rawSSRT[diff_SSRT_rows_ssrt,]$ID))
colnames(outliers_ssrt_count) <- c("ID", "outliers_ssrt_count")

# create new "outliers4" vector
outliers_ssrt_logical <- row.names(df_SSRT) %in% diff_SSRT_rows_ssrt
```

## View omitted runs
### Both scans
```{r Full table of omitted runs, echo=FALSE}
# NOTE: This is the correct list of omitted runs to use. There are 54 cases total. REV004 run 1 and REV059 run 1 were previously not flagged but should have been. REV004 has too many wrongGo's and REV059 has pctInhib > 75. 
df_omitted_runs <- cbind(df_SSRT, outliers_pctInhib_logical, outliers_noResponse_logical, outliers_wrongGo_logical, outliers_ssrt_logical)
df_omitted_runs_all <- filter(df_omitted_runs, (outliers_pctInhib_logical == TRUE | outliers_noResponse_logical == TRUE | outliers_wrongGo_logical == TRUE | outliers_ssrt_logical == TRUE))
df_omitted_runs_all <- sort(df_omitted_runs_all[,c(1,3)])
kable(df_omitted_runs_all, caption = "Full list of scanner runs to omit from analysis", row.names = FALSE)
```
A total of `r length(unique(as.numeric(df_omitted_runs_all$ID)))` participants have at least one run that will be excluded from analysis.  

### Base scan only
```{r table of omitted baseline runs, echo = FALSE}
df_omitted_runs_base <- filter(df_omitted_runs, (time == 'run1' | time == 'run2' | outliers_pctInhib_logical == TRUE | outliers_noResponse_logical == TRUE | outliers_wrongGo_logical == TRUE | outliers_ssrt_logical == TRUE))
df_omitted_runs_base <- sort(df_omitted_runs_base[,c(1,3)])
kable(df_omitted_runs_base, caption = "List of baseline scanner runs to omit from analysis", row.names = FALSE)
```
A total of `r length(unique(as.numeric(df_omitted_runs_base$ID)))` participants have at least one run at baseline that will be excluded from analysis.  

### End scan only
```{r table of omitted endpoint runs, echo = FALSE}
df_omitted_runs_end <- filter(df_omitted_runs, (time == 'run13' | time == 'run14' | outliers_pctInhib_logical == TRUE | outliers_noResponse_logical == TRUE | outliers_wrongGo_logical == TRUE | outliers_ssrt_logical == TRUE))
df_omitted_runs_end <- sort(df_omitted_runs_end[,c(1,3)])
kable(df_omitted_runs_end, caption = "List of endpoint scanner runs to omit from analysis", row.names = FALSE)
```
A total of `r length(unique(as.numeric(df_omitted_runs_end$ID)))` participants have at least one run at endpoint that will be excluded from analysis.  

```{r Create a table of omitted runs}
# See omitted
dfs <- list(outliers_pctInhib_count, outliers_noResponse_count, outliers_wrongGo_count, outliers_ssrt_count)
outliers_tableFull <- plyr::join_all(dfs, by = "ID")
outliers_table <- outliers_tableFull[which(outliers_tableFull$outliers_ssrt_count != 0),]
kable(outliers_table, caption = "Runs Omitted, Base & End Scans (columns are cumulative)")
summary(outliers_tableFull$outliers_ssrt_count)
```

## Notes on problem runs

- 134 - kept switching correct/incorrect direction presses.  
- 82 - switched buttons 1/2 way through run 7.  
- 91 - stopped trying for last part of run 3. Repeatedly pressing same key (not an assigned key).  
- 26 - Participant in experimental condition, but has 0% inhibition during all training runs.  
- 51 - Why doesn't 51 have the base scan SSRTs?   
    + Can't be calculated due to high number of non-responses and wrong-gos.  
- 138 - Why doesn't 138 have the base scan SSRTs?   
    + Can't be calculated due to high number of wrong-gos.  
    
    
    
```{r Subset only the base scan data and convert long to wide}
# select only scan data (get rid of training data)
df_SSRT <- subset(df_SSRT,time %in% c("run1", "run2"))[,c("ID","time","SSRT")] %>%
  spread(time, SSRT)

# re-name SSRT vars to be more specific
names(df_SSRT)[names(df_SSRT)=="run1"] <- "SSRT_run1"
names(df_SSRT)[names(df_SSRT)=="run2"] <- "SSRT_run2"

# Create vars that represent mean SSRT across available runs for and endpoint scans
df_SSRT$SSRT_base_mean <- rowMeans(df_SSRT[,c("SSRT_run1","SSRT_run2")], na.rm = TRUE)
```

## Write relevant output for Brendan's FYP to .csv file
```{r}
# list of omitted runs
write.csv(df_omitted_runs, file = paste0(outputDir, "/SST_ScanBx_omitted_runs.csv"), row.names = FALSE)

write.csv(df_SSRT, file = paste0(outputDir, "/SSRT_base_mean.csv"), row.names = FALSE)
```
